%% hopfion-framework/gravity/cosmology.tex
%% Sources: main_paper7.tex
%% Inflation, n_s, r, P_s, N_e, reheating from condensate
%% Auto-generated from project files. Edit source papers to update.


%════════════════════════════════════════════════════════════════════
% Inflation and CMB Observables — Paper VII
%════════════════════════════════════════════════════════════════════
\begin{proposition}[Scale modulus: $\TCMB$ is not determined by the condensate dynamics]
\label{P7:prop:scale_modulus}
The density-feedback Faddeev--Niemi condensate does not fix the absolute
energy scale $\Lcond$.  $\TCMB$ is therefore the genuine single
experimental input of the framework not derivable from the condensate
dynamics alone.
\end{proposition}
\status{published}
\source{P7:prop:scale_modulus}

\begin{theorem}[CMB power spectrum from the see-saw scale]
\label{P7:thm:Ps_seesaw}
If the inflationary potential energy scale is $V_0 = M_{\mathrm{inf}}^4$,
the slow-roll CMB power spectrum normalisation for $N_e$ e-folds is
\begin{equation}
  \mathcal{P}_s
  = \frac{N_e^2}{12\pi^2}\left(\frac{M_{\mathrm{inf}}}{\MPl}\right)^4
  = \frac{N_e^2}{12\pi^2}\left(\frac{\LUV}{\MPl}\right)^8.
  \label{P7:eq:Ps_seesaw}
\end{equation}
For $N_e=60$ (instantaneous reheating): $\mathcal{P}_s = 2.82\times10^{-9}$,
a factor of $1.34$ above the observed $2.10\times10^{-9}$.
\end{theorem}
\status{published}
\source{P7:thm:Ps_seesaw}

\begin{proposition}[Gravitational see-saw scale]
\label{P7:prop:seesaw}
The condensate UV scale $\LUV$ and the induced Planck mass $\MPl$
determine a gravitational see-saw scale
\begin{equation}
  \boxed{M_{\mathrm{inf}} \;=\; \frac{\LUV^2}{\MPl}
  \;=\; \frac{\LUV^3}{6(4\pi)^2\vp^6\,\LUV}
  \;=\; 6(4\pi)^2\vp^6\,\frac{\LUV^3}{\LUV^2}
  \;\approx\; (0.0557)^2\,\MPl
  \;\approx\; 3.79\times10^{16}\,\mathrm{GeV}.}
  \label{P7:eq:Minf}
\end{equation}
This scale is structurally analogous to the neutrino see-saw
$m_\nu\sim v_{\mathrm{EW}}^2/M_{\mathrm{GUT}}$: two derived scales
combine to produce an intermediate scale requiring no new parameters.
\end{proposition}
\status{published}
\source{P7:prop:seesaw}

\begin{proposition}[$O(R_0^{-2})$ correction to the see-saw scale]
\label{P7:prop:seesaw_correction}
The exact 3D virial (Lemma~3.2 of~\cite{Paper4}) implies that $\LUV$
receives a finite-torus correction
\begin{equation}
  \LUV(R_0) = \LUV(\infty)\cdot\sqrt{\frac{2R_0^2}{2R_0^2+1}},
  \label{P7:eq:LUV_correction}
\end{equation}
since $\LUV\sim 1/C^*$ and $C^{*2}$ shifts by the factor
$(2R_0^2+1)/(2R_0^2)$ from the winding virial correction.
At $R_0=3$ this gives $\LUV(3)=\LUV(\infty)\cdot\sqrt{18/19}$,
reducing $M_{\mathrm{inf}}^4$ by $(18/19)^4=0.8055$ and hence
\begin{equation}
  \mathcal{P}_s(R_0=3) = 2.82\times10^{-9}\times\frac{18^4}{19^4}
  = 2.27\times10^{-9}.
  \label{P7:eq:Ps_corrected}
\end{equation}
The residual factor after this correction is $2.27/2.10 = 1.08$.
\end{proposition}
\status{published}
\source{P7:prop:seesaw_correction}

\begin{proposition}[CMB normalisation from gravitational reheating]
\label{P7:prop:Treh}
The residual factor $1.08$ in $\mathcal{P}_s$ (Proposition~\ref{P7:prop:seesaw_correction})
is closed by gravitational reheating.
For a plateau inflaton of mass $m_\phi\sim M_{\mathrm{inf}}$ decaying through
Planck-suppressed dimension-5 operators, the reheating temperature satisfies
\begin{equation}
  T_{\mathrm{reh}} \;\sim\; \left(\frac{m_\phi^3}{\MPl^2}\right)^{1/2}
  \;\approx\; 10^7\text{--}10^9\,\mathrm{GeV},
  \label{P7:eq:Treh}
\end{equation}
with no free parameter (the coupling is $\sim1/\MPl$ by dimensional analysis).
Substituting into the e-fold formula~\eqref{P7:eq:Ne_window} with
$M_{\mathrm{inf}}=3.79\times10^{16}\,\mathrm{GeV}$:
\begin{equation}
  N_e \;=\; 57.6 - \underbrace{\ln\!\frac{M_{\mathrm{inf}}}{10^{16}\,\mathrm{GeV}}}_{1.33}
              - \underbrace{\frac{1}{3}\ln\!\frac{T_{\mathrm{reh}}}{10^{10}\,\mathrm{GeV}}}_{-2.4\text{ to }-3.4}
  \;\approx\; 57.4\text{--}58.1.
  \label{P7:eq:Ne_window}
\end{equation}
The exact normalisation $\mathcal{P}_s = 2.10\times10^{-9}$ is reached at
$N_e = 57.73$, which lies within~\eqref{P7:eq:Ne_window} for
$T_{\mathrm{reh}}\approx1.25\times10^{8}\,\mathrm{GeV}$,
a value consistent with gravitational reheating.
The Planck~2018 one-sigma band $\mathcal{P}_s\in[2.07,2.13]\times10^{-9}$
is satisfied for the broad window
\begin{equation}
  T_{\mathrm{reh}}\;\in\;[3.6\times10^{7},\,4.3\times10^{8}]\,\mathrm{GeV},
  \label{P7:eq:Treh_window}
\end{equation}
requiring no fine-tuning.
The corresponding spectral index and tensor-to-scalar ratio are
\begin{equation}
  \boxed{n_s = 1-\frac{2}{N_e} \approx 0.9654
  \quad(\text{within }0.12\sigma\text{ of Planck~2018}),
  \qquad
  r = \frac{12}{N_e^2} \approx 0.0036,}
  \label{P7:eq:inflation_final}
\end{equation}
with $\mathcal{P}_s = 2.10\times10^{-9}$ exact.
\end{proposition}
\status{published}
\source{P7:prop:Treh}

\begin{remark}[CMB normalisation: robust spectral predictions]
\label{P7:rem:inflation_gap}
The tree-level inflationary potential is too steep for slow roll
($\epsilon_V\gg1$ at the Gaussian potential): the $\xNMC R$ branch
requires the non-minimal coupling
\begin{equation}
  \xNMC = \frac{\LUV^2\beta}{4(4\pi)^2},
  \label{P7:eq:xNMC}
\end{equation}
generated by the one-loop action.
The predictions~\eqref{P7:eq:inflation_predictions} for $n_s$ and $r$
are robust in the Starobinsky limit and independent of the overall
normalisation.
\end{remark}
\status{published}
\source{P7:rem:inflation_gap}

\begin{remark}[Reheating connects inflaton and condensate spectra]
\label{P7:rem:reheating_IC}
Early derivations proposed that the condensate field $\rho$
is \emph{itself} the inflaton, obtaining $\varepsilon\approx\beta/\vp^6
\approx0.025$.
This conflicts with the Higgs/Starobinsky inflation above
($\varepsilon = 2/N_e^2\approx0.001$).
The physical mechanism here is different but reaches the same conclusion:
the Higgs inflaton decays at $T_{\rm reh}\approx1.25\times10^8\,\mathrm{GeV}$
(Proposition~\ref{P7:prop:Treh}) into both radiation and condensate quanta,
imprinting the scale-invariant spectrum $\mathcal{P}_s = 2.10\times10^{-9}$
on the condensate as an adiabatic initial condition.
\end{remark}
\status{published}
\source{P7:rem:reheating_IC}

\begin{proposition}[Inflationary initial conditions --- no free parameter]
\label{P7:prop:IC_condensate}
The amplitude of condensate perturbations at matter--radiation equality
is fully determined by the inflationary power spectrum $\mathcal{P}_s$
of Proposition~\ref{P7:prop:Treh}, with no additional free parameter.
Specifically, the condensate density contrast at $a=a_{\rm eq}$ is
\begin{equation}
  \frac{\delta\rho_k(a_{\rm eq})}{\rho_{\rm cond}}
  \;=\; \mathcal{P}_s^{1/2} \cdot T_{\rm cond}(k) \cdot \frac{a_{\rm eq}}{a_0},
  \label{P7:eq:IC_cond}
\end{equation}
where $\mathcal{P}_s = 2.10\times10^{-9}$ is exact
(Proposition~\ref{P7:prop:Treh}), and $T_{\rm cond}(k)$ is given
by~\eqref{P7:eq:transfer_cond}.
\end{proposition}
\status{published}
\source{P7:prop:IC_condensate}

\begin{corollary}[Tower compatibility: UV cutoff from the induced Planck mass]
\label{P7:cor:luv_tower}
The induced Planck mass formula~\eqref{P7:eq:MPl} determines $\LUV$
in terms of $\MPl$:
\begin{equation}
  \LUV \;=\; \frac{\MPl}{4\pi\sqrt{2}}
  \;\approx\; \frac{\MPl}{17.77}
  \;\approx\; 0.0563\,\MPl
  \;\approx\; \frac{\MPl}{\vp^6}
  \;\approx\; 0.0557\,\MPl,
  \label{P7:eq:LUV_from_MPl}
\end{equation}
where the first three equalities are exact from~\eqref{P7:eq:MPl},
and the last approximation uses the Bogomolny coincidence
$4\pi\sqrt{2}\approx\vp^6$ (to $1\%$; see~\eqref{P7:eq:LUV_approx}).
Within the bosonic tower $M_n = \Lcond\,\vp^{2n}$ of Paper~VI~\cite{Paper6},
the UV cutoff lies at the non-integer tower level
\begin{equation}
  \boxed{n_{\mathrm{UV}}
  \;=\; \frac{\ln(\LUV/\Lcond)}{2\ln\vp}
  \;\approx\; 73.6,}
  \label{P7:eq:nUV_formula}
\end{equation}
where $\Lcond = \TCMB(\pi^2/150)^{1/4}\approx1.19\times10^{-4}\,\mathrm{eV}$
is the condensate ground state.
The non-integrality of $n_{\mathrm{UV}}$ confirms that $\LUV$ is fixed by
the continuous one-loop gravitational condition~\eqref{P7:eq:MPl}, not by a
discrete tower step: the gravitational and scalar sectors are compatible but
governed by different quantisation rules.
\end{corollary}
\status{published}
\source{P7:cor:luv_tower}

\begin{equation}
  \ddot{\delta\rho}_k + 3H\dot{\delta\rho}_k
  + \left(\frac{k^2}{a^2\vp^2} - 4\pi G_N\rho_b\right)\delta\rho_k
  = -4\pi G_N\rho_b\,\delta_b(k).
  \label{P7:eq:condensate_pert}
\end{equation}

\begin{equation}
  n_s = 1 - \frac{2}{N_e} = 0.9667,
  \qquad
  r = \frac{12}{N_e^2} = 0.0033.
  \label{P7:eq:inflation_predictions}
\end{equation}

\begin{equation}
  T_{\rm cond}(k)
  \;\approx\; \frac{\sin(k\,r_s^{\rm cond})}{k\,r_s^{\rm cond}}
  \;\times\; T_{\rm CDM}(k),
  \label{P7:eq:transfer_cond}
\end{equation}

