%% hopfion-framework/gravity/dark_sector.tex
%% Sources: main_paper7.tex
%% Cosmological constant, dark energy w_a, dark matter c_s, BAO, Vainshtein
%% Auto-generated from project files. Edit source papers to update.


%════════════════════════════════════════════════════════════════════
% Cosmological Constant and Dark Energy — Paper VII
%════════════════════════════════════════════════════════════════════
When $\rho$ is frozen at $\rinfty$ ($\dot\rho=0$), the equation of
state is $w=-1$ exactly, reproducing $\Lambda$CDM.
The dark energy scalar mass at the potential minimum is
\begin{equation}
  m_\xi^2 = \vp^{20}\,\Lobs\,\MPl^4,
  \label{P7:eq:mxi}
\end{equation}
giving $m_\xi\approx H_0\approx10^{-33}\,\mathrm{eV}$, the Hubble scale.

\begin{proposition}[EFT self-consistency and UV naturalness]
\label{P7:prop:eft_naturalness}
The effective field theory defined by the parent action~\eqref{P7:eq:parent_action}
is self-consistent for all energies $E < \LUV$: every loop correction
from matter running in the condensate background is suppressed by
$(E/\LUV)^2$ relative to the leading term, so no prediction of this
paper requires input from a UV completion above $\LUV$.
Specifically:
\begin{enumerate}[noitemsep,label=\emph{(\roman*)}]
\item \textbf{Inflationary sector.} The inflationary potential is
  evaluated at $\varphi_c\lesssim\MPl$ (Section~\ref{sec:inflation}),
  well below $\LUV\approx0.0557\,\MPl$ in energy per degree of freedom;
  corrections are $O(H_{\mathrm{inf}}^2/\LUV^2)\sim10^{-7}$.
\item \textbf{Dark energy sector.} The dark energy mass
  $m_\xi\approx H_0\sim10^{-33}\,\mathrm{eV}$ satisfies
  $m_\xi\ll\LUV$ by 52 orders of magnitude; the attractor
  solution $\rinfty=\vp/\beta$ and the thawing relation
  $w_a=-3(1+w_0)$ are independent of the UV completion.
\item \textbf{Gravitational sector.} The induced Planck mass
  $\MPl^2=\LUV^2/[6(4\pi)^2\vp^6]$ is set at the scale $\LUV$
  itself; no physics above $\LUV$ is needed to determine $\MPl$.
  The Planck length $\ell_{\mathrm{Pl}}=1/\MPl$ is emergent, not
  a fundamental input.
\item \textbf{Cassini and WEP sectors.} Both the Vainshtein~\cite{Vainshtein1972} screening
  radius $r_V\approx9.3\times10^6\,\mathrm{AU}$ (Theorem~\ref{P7:thm:cassini})
  and the WEP instanton suppression $\eta_A=e^{-AS_1}$
  (Section~\ref{sec:wep}) depend on $\LUV$ and $\MPl$ only through
  the combination $m_\xi^2=\vp^{20}\Lobs\MPl^4$, which is
  fixed entirely within the EFT below $\LUV$.
\end{enumerate}
\end{proposition}
\status{published}
\source{P7:prop:eft_naturalness}

\begin{remark}[Status of the UV completion]
\label{P7:rem:uv_completion_status}
Proposition~\ref{P7:prop:eft_naturalness} establishes that the framework
is UV-safe in the sense relevant for its predictions: no measurement
described in this paper probes scales above $\LUV\approx0.0557\,\MPl$.
An explicit UV completion above $\LUV$ --- whether string embedding,
asymptotic safety, or another mechanism --- would be needed to address
questions about Planck-scale scattering or the trans-Planckian problem
for inflation, but such a completion does not affect the results here.
The characteristic condensate length scale $\ell_\mathrm{cond}=1/\LUV
\approx\vp^6\,\ell_{\mathrm{Pl}}\approx17.9\,\ell_{\mathrm{Pl}}$
is super-Planckian, consistent with the EFT being valid for
$\ell>\ell_\mathrm{cond}$.
\end{remark}
\status{published}
\source{P7:rem:uv_completion_status}

\begin{corollary}[Topological origin of the Vainshtein radius]
\label{P7:cor:vainshtein_topology}
The Vainshtein radius $r_V\approx9.3\times10^6\,\mathrm{AU}$ is
determined by the Hopf charge $Q=2$ of the condensate vacuum through
the following chain, with no free parameters:
\begin{enumerate}[noitemsep,label=\emph{(\roman*)}]
\item The $Q=2$ Hopfion vacuum, established in~\cite{Paper1}, has
  topological charge $Q_{\mathrm{condensate}}=10$ fixed by the
  WZW quantum-group order $\mathrm{ord}(q_{2I})=2(k+2)|_{k=3}=10$
  (Theorem~5.9 of~\cite{Paper1}).
\item The dark-energy scalar mass is determined by $Q_{\mathrm{condensate}}$:
  $m_\xi^2 = \vp^{2Q_{\mathrm{condensate}}}\,\Lobs\,\MPl^4
  = \vp^{20}\,\Lobs\,\MPl^4$ (equation~\eqref{P7:eq:mxi}).
\item The Brans--Dicke parameter is $\oBD=\vp^{12}/(3\beta)
  = \vp^{2(Q_{\mathrm{condensate}}-Q_{\mathrm{Hopfion}}\cdot(k+2))}/(3\beta)$,
  where $\vp^{12}=(\lam)^2$ is the square of the Bogomolny parameter.
\item Substituting both into the Vainshtein formula (Theorem~\ref{P7:thm:cassini})
  yields $r_V\propto r_S^{1/3}\,\vp^{(12-20)/3}=r_S^{1/3}\,\vp^{-8/3}$,
  so $r_V$ scales as $\vp^{-8/3}$ relative to the Schwarzschild radius,
  entirely determined by the golden ratio and the condensate topological charge.
\end{enumerate}
The Vainshtein radius is therefore a topological invariant of the $Q=2$
Hopfion condensate: it is fixed by the Hopf charge $Q_{\mathrm{Hopfion}}=2$
through the quantum-group order $Q_{\mathrm{condensate}}=10$ and the
Bogomolny parameter $\lam=\vp^6$, with no additional input.
This resolves the open problem stated in Paper~I~\cite{Paper1}.
\end{corollary}
\status{published}
\source{P7:cor:vainshtein_topology}

\begin{remark}[Lorentz violation and its recovery]
\label{P7:rem:lorentz}
Axiom~A1 introduces a preferred direction $\hat{e}_r = \nabla\rho/|\nabla\rho|$
that breaks global Lorentz invariance fundamentally.  The graviton mass
$m_g^2\propto1/\vp^6(1+\beta\rho_\infty)$ is Lorentz-breaking in the same
sense.  However, at high local density $\epsilon=\beta\rho\gg1$, the
suppression factor $S_{\mathrm{eff}}=S(\theta)/(1+\beta\rho)\to0$:
the preferred direction decouples from local physics and local Lorentz
invariance is restored to precision $O((\bst\rho)^{-1})$.
At Solar System densities $(\bst\rho_\odot)^{-1}\sim10^{-6}$, so all
PPN tests recover standard GR values at that level~\cite{Paper1}.
Conversely, in cosmic voids where $\rho\ll1/\bst$, the preferred
direction is unsuppressed and Lorentz-violating signals of order
$\sim10^{-3}$ are predicted, potentially accessible to VLBI
astrometry~\cite{Paper1}.  This density-dependent recovery is the
field-theoretic analogue of the Vainshtein mechanism and is consistent
with the Cassini resolution (Theorem~\ref{P7:thm:cassini}).
\end{remark}
\status{published}
\source{P7:rem:lorentz}

\begin{remark}[Chameleon field interpretation]
\label{P7:rem:chameleon}
The density-dependent suppression of Axiom~A2,
$S_{\mathrm{eff}}(\theta,\rho) = \sin^4\!\theta/[\vp^6(1+\beta\rho)]$,
is precisely the chameleon mechanism~\cite{KhouryWeltman2004}: the scalar $\rho$
acquires a density-dependent effective coupling
$\beta_{\mathrm{eff}}(\rho) = \beta/(1+\beta\rho)$
that runs from the UV value $\beta$ at vacuum density down to
$\beta_{\mathrm{eff}}\approx1/\rho$ in dense environments ($\beta\rho\gg1$).

This single mechanism simultaneously explains three features of the framework:
\begin{enumerate}[noitemsep,label=\emph{(\roman*)}]
  \item \textbf{Cassini resolution.}  The screened Brans-Dicke parameter
    in a dense region becomes $\oBD^{\mathrm{eff}} = \oBD(1+\beta\rho_\odot)$,
    enhanced over the vacuum value.  For $\beta\rho_\odot\gg1$ this is
    arbitrarily large, satisfying the Cassini constraint without requiring
    $\beta$ to be small; the Vainshtein~\cite{Vainshtein1972} resolution of
    Theorem~\ref{P7:thm:cassini} is complementary and operates at
    cosmological scales.
  \item \textbf{Local Lorentz recovery.}  At high density
    $S_{\mathrm{eff}}\to0$, so the preferred direction $\hat{e}_r$
    decouples from local physics; this is precisely the high-$\rho$
    recovery described in Remark~\ref{P7:rem:lorentz}.
  \item \textbf{Self-consistency.}  In~\cite{Paper1} the feedback
    functional $\Jfb = \int\mathrm{kern}/(1+\bst\,\mathrm{kern})\,\mathrm{dvol}$
    is noted to be a Born--Infeld saturation and chameleon screening
    simultaneously (Remark~4.3 of~\cite{Paper1}).
    Here the same structure operates at the cosmological level:
    the chameleon effective coupling $\beta_{\mathrm{eff}}(\rho)$
    connects the condensate-scale feedback ($\bst\approx0.452$) to
    the gravitational screening at Solar System and cosmological scales.
\end{enumerate}
The chameleon and Vainshtein mechanisms are therefore not competing
explanations of the Cassini resolution: the chameleon accounts for the
density-dependent coupling suppression in the nonlinear regime at
$r\ll r_V$, while the Vainshtein~\cite{Vainshtein1972} radius
(equation~\eqref{P7:eq:rV_exact}) sets the
scale at which nonlinear terms begin to dominate.
\end{remark}
\status{published}
\source{P7:rem:chameleon}

\begin{equation}
  ds_{\mathrm{ac}}^2 = \rho_0(r)\cdot ds_{\mathrm{Schwarzschild}}^2,
  \label{P7:eq:acoustic_schwarz}
\end{equation}

\begin{equation}
  c_s^2
  = 1 + \frac{\rinfty K'(\rinfty)}{K(\rinfty)}
  = 1 - \frac{\beta\rinfty}{1+\beta\rinfty}
  = 1 - \frac{\vp}{\vp^2}
  = \frac{1}{\vp^2}.
  \label{P7:eq:cs_exact}
\end{equation}

\begin{equation}
  c_s^2 = \frac{\partial P}{\partial\rho}\bigg|_{\rho_0}
        = 1 + O(\beta^3)
  \label{P7:eq:cs_schwarz}
\end{equation}

\begin{theorem}[Exact golden sound speed]
\label{P7:thm:cs}
The sound speed of scalar perturbations of the density-feedback condensate
at the attractor $\rinfty = \vp/\beta$ is
\begin{equation}
  \boxed{c_s \;=\; \frac{1}{\vp},}
  \label{P7:eq:cs_value}
\end{equation}
an exact result with no free parameters.
\end{theorem}
\status{published}
\source{P7:thm:cs}

\begin{equation}
  \delta c_s^2 = -\frac{\beta^3}{4(1+\vp)} \approx -4.2\times10^{-5}
  \quad\text{at }r\sim r_s.
  \label{P7:eq:delta_cs}
\end{equation}

\begin{equation}
  \frac{dw}{da}\bigg|_{a=1}
  \;=\; \frac{d(1+w)}{da}\bigg|_{a=1}
  \;=\; 6(1+w_0).
  \label{P7:eq:dwa_slope}
\end{equation}

\begin{proposition}[Condensate is pressureless on galactic scales]
\label{P7:prop:CDM_limit}
The condensate sound speed $c_s = 1/\vp$ (Theorem~\ref{P7:thm:cs}) implies
a Jeans length
\begin{equation}
  \lambda_J
  \;=\; \frac{2\pi\,c_s}{\sqrt{4\pi G_N\rho_{\rm cond}}}
  \;\approx\; \frac{2\pi\,c/\vp}{\sqrt{4\pi G_N \times 0.26\,\rho_{\rm crit}}}
  \;\approx\; 2.8\times10^4\,\mathrm{Mpc},
  \label{P7:eq:lambda_J}
\end{equation}
where $\rho_{\rm cond}\approx0.26\,\rho_{\rm crit}$ is the observed
dark-matter density (Planck~2018~\cite{Planck2018}), an observational
input to this sector alongside $\TCMB$ and $m_e$.
On all galactic and cluster scales ($r \ll \lambda_J$), the condensate
is effectively pressureless and behaves as cold dark matter.
Rotation curves are flat by the same mechanism as CDM.
\end{proposition}
\status{published}
\source{P7:prop:CDM_limit}

\begin{proposition}[$G_{\rm eff}(r)$ in the screened halo]
\label{P7:prop:Geff}
The BD scalar coupling to matter is characterised by
\begin{equation}
  \alpha_{\rm BD}
  \;=\; \frac{2\beta^2}{2\omega_{\rm BD}+3}
  \;\approx\; \frac{6\beta^3}{2\vp^{12}}
  \;\approx\; 8.5\times10^{-4}.
  \label{P7:eq:alpha_BD}
\end{equation}
The Vainshtein radius of a Milky-Way-mass galaxy
($M\sim6\times10^{10}\,M_\odot$) is
\begin{equation}
  r_V^{\rm MW}
  \;=\; r_V^\odot\times\!\left(\frac{M_{\rm MW}}{M_\odot}\right)^{\!1/3}
  \;\approx\; 0.045\,\mathrm{kpc}\times3915
  \;\approx\; 176\,\mathrm{kpc},
  \label{P7:eq:rV_MW}
\end{equation}
placing the entire stellar disk ($r\lesssim15\,\mathrm{kpc}\ll r_V^{\rm MW}$)
deep inside the Vainshtein sphere.
The effective Newton constant at flat-rotation-curve radii $r\lesssim30\,\mathrm{kpc}$
is
\begin{equation}
  \frac{G_{\rm eff}(r)}{G_N}
  \;=\; 1 + \alpha_{\rm BD}\!\left(\frac{r}{r_V^{\rm MW}}\right)^{\!3/2}
  \;\leq\; 1 + 6\times10^{-5}
  \qquad(r\leq30\,\mathrm{kpc}),
  \label{P7:eq:Geff_screened}
\end{equation}
indistinguishable from $G_N$ at the level of rotation-curve measurements.
\end{proposition}
\status{published}
\source{P7:prop:Geff}

\begin{remark}[Rotation curves from condensate halo profile]
\label{P7:rem:rotation_curves_halo}
The condensate acts as cold dark matter on galactic scales
(Proposition~\ref{P7:prop:CDM_limit}) and $G_{\rm eff}(r) = G_N$
to $6\times10^{-5}$ at rotation-curve radii
(Proposition~\ref{P7:prop:Geff}).
Rotation curves are therefore flat by exactly the same mechanism as
CDM: the condensate forms an NFW-like gravitational halo
through the standard gravitational instability, with the baryonic
disk sitting inside a dark halo of condensate.
No additional mechanism (modified gravity, $G_{\rm eff}$ variation,
or Vainshtein transition effects) is required at galactic scales.

The leading condensate correction to the Newtonian rotation curve is
a pressure-gradient term of order $(r/\lambda_J)^2\lesssim5\times10^{-11}$
at $r\leq r_{\rm halo}$, completely negligible.
The gravitational coupling correction is $\alpha_{\rm BD}(r/r_V)^{3/2}
\lesssim6\times10^{-5}$ at $r\leq30\,\mathrm{kpc}$, also negligible.

The primary \emph{new} prediction distinguishing the condensate from
standard CDM is not in the rotation curves but in the large-scale
matter power spectrum: the BAO peak shifts by factor $\vp$
to $k_{\rm BAO}^{\rm cond}\approx0.0346\,\mathrm{Mpc}^{-1}$
(equation~\eqref{P7:eq:kBAO_shift}), falsifiable with DESI~DR2 and Euclid.
\end{remark}
\status{published}
\source{P7:rem:rotation_curves_halo}

\begin{equation}
  \boxed{w_a \;=\; -3(1+w_0),}
  \label{P7:eq:wa_derived}
\end{equation}

\begin{theorem}[Thawing quintessence relation]
\label{P7:thm:thawing}
If $\rho$ has not fully frozen at the attractor ($\dot\rho_0\neq0$),
the CPL equation-of-state parameters satisfy
\begin{equation}
  \boxed{w_a \;=\; -3(1+w_0),}
  \label{P7:eq:thawing}
\end{equation}
where $w_a\equiv-dw/da\big|_{a=1}$ and $w_0=w(a=1)$.
This is an exact result at leading order in the slow-roll expansion
$\dot\rho^2\ll\vp^8\Lobs$ (i.e.\ $|1+w_0|\ll1$).
For the DESI~DR1 value $w_0=-0.727\pm0.067$, the prediction is
$w_a=-0.819$, within $0.80\sigma$ of the measured
$w_a=-1.05^{+0.31}_{-0.27}$~\cite{DESI2024}.
\end{theorem}
\status{published}
\source{P7:thm:thawing}

\begin{remark}[DESI consistency and the frozen-field tension]
\label{P7:rem:desi_consistency}
The DESI~DR1 central values $w_0=-0.727\pm0.067$, $w_a=-1.05^{+0.31}_{-0.27}$
give $-3(1+w_0)=-0.819$ versus $w_a^\mathrm{DESI}=-1.05$: a $0.80\sigma$
agreement.  The frozen-field limit $w_0=-1$, $w_a=0$ is $\approx4\sigma$ from
the DESI central values.
If DESI~DR2 confirms $w_0\neq-1$ at $>3\sigma$, the framework
accommodates this via a nonzero initial displacement
$\delta\rho_0=\rinfty-\rho_\mathrm{today}\sim\sqrt{\Lobs}/\MPl^2$,
a natural scale with no fine-tuning.
The one-parameter prediction $w_a=-3(1+w_0)$ is falsifiable:
any measurement of $w_0$ uniquely pins $w_a$.
\end{remark}
\status{published}
\source{P7:rem:desi_consistency}

