\documentclass[11pt,a4paper]{article}

%─── Packages ─────────────────────────────────────────────────────────────────
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage[bookmarks=false]{hyperref}
\usepackage{array}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{float}
\usepackage{longtable}
\geometry{top=2.5cm,bottom=2.8cm,left=2.5cm,right=2.5cm}

%─── Theorem environments ─────────────────────────────────────────────────────
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{conjecture}{Conjecture}

%─── Macros ───────────────────────────────────────────────────────────────────
\newcommand{\vp}{\varphi}
\newcommand{\lam}{\lambda}
\newcommand{\bst}{\beta^{*}}
\newcommand{\sinW}{\sin^{2}\!\theta_{W}}
\newcommand{\TCMB}{T_{\mathrm{CMB}}}
\newcommand{\vEW}{v_{\mathrm{EW}}}
\newcommand{\Lcond}{\Lambda_{\mathrm{cond}}}
\newcommand{\LUV}{\Lambda_{\mathrm{UV}}}
\newcommand{\MPl}{M_{\mathrm{Pl}}}
\newcommand{\LQCD}{\Lambda_{\mathrm{QCD}}}
\newcommand{\ERy}{E_{\mathrm{Ry}}}
\newcommand{\aem}{\alpha_{\mathrm{em}}}
% Tower level macro
\newcommand{\nlvl}[1]{n\!\left(#1\right)}
% IE abbreviation
\newcommand{\IE}{\mathrm{IE}}

%─── Colours ──────────────────────────────────────────────────────────────────
\definecolor{darkgreen}{RGB}{0,120,60}
\definecolor{darkred}{RGB}{160,20,20}
\definecolor{darkblue}{RGB}{0,40,140}
\definecolor{darkorange}{RGB}{180,80,0}

%══════════════════════════════════════════════════════════════════════════════
\title{\textbf{The Golden-Spiral as a Universal Mass Hierarchy Map:\\
  From Condensate Scale to Chemical Periodicity}
\\[0.6em]
{\large Companion Paper XI to the Density-Feedback
Faddeev--Niemi Hopfion Series}
\\[0.6em]
\large Preprint --- April 2026}
\author{Frederick Manfredi}

\date{2026}
%══════════════════════════════════════════════════════════════════════════════

\begin{document}
\maketitle

\paragraph*{Units and conventions.}
Natural units $\hbar = c = k_B = 1$ throughout.
Energies in eV, MeV, or GeV.
$\MPl = 1.22\times10^{19}\,\mathrm{GeV}$ (unreduced Planck mass,
consistent with Papers~I--VII).
The condensate scale is
$\Lcond = \TCMB(\pi^2/150)^{1/4} = 1.1895\times10^{-4}\,\mathrm{eV}$.
The fine-structure constant and electron mass are framework outputs:
$\aem^{-1} = 137.035998$ (Paper~IV~\cite{Paper4}, four-term formula, $5\times10^{-7}\%$) and
$m_e = 0.51100\,\mathrm{MeV}$ (Paper~IV~\cite{Paper4}).

%─── Abstract ─────────────────────────────────────────────────────────────────
\begin{abstract}
The density-feedback Faddeev--Niemi Hopfion framework
of Papers~I--X~\cite{Paper1,Paper2,Paper3,Paper4,Paper5,Paper6,Paper7,Paper8,Paper9,Paper10}
derives $\alpha_\mathrm{em}^{-1}=137.035998$ and $m_e=0.511\,\mathrm{MeV}$
from a single experimental input $\TCMB$ with no free parameters
(Paper~XII~\cite{Paper12} proves the one-parameter chain).
We show that these two derived quantities, together with the
$\vp$-tower $m_n = \Lcond\,\vp^{-2n}$, place \emph{all} known energy
scales --- particle masses, gauge-boson masses, QCD, electroweak,
UV, and Planck scales, as well as the first ionisation energies of
the chemical elements --- on a single logarithmic spiral in which
one revolution corresponds to six tower levels and the radial
coordinate is $r = \log(1 + 0.8|n|)$.

The central result is a \textbf{Corollary of Papers~III and~IV}:
the Rydberg energy $\ERy = \aem^2\,m_e/2 = 13.6057\,\mathrm{eV}$
is a \emph{fixed, calculable tower level}
$n(\ERy) = -12.102$, with no free parameters.
Since $\aem$ and $m_e$ are both derived from $\TCMB$ alone
(up to the $0.22\%$ thick-torus residual of Paper~IV),
the entire atomic energy scale is a prediction of the condensate.

Three structural observations follow from placing the
periodic table on the spiral:
(i)~the visible electromagnetic spectrum ($1.77$--$3.1\,\mathrm{eV}$)
coincides with the pure tower level
$\Lcond\,\vp^{20} = 1.799\,\mathrm{eV}$
to $1.7\%$, linking the optical window directly to the condensate
scale via the same level index as the electron mass;
(ii)~hydrogen and oxygen are near-degenerate on the spiral
($\Delta n = 0.0015$, $\Delta\IE/\IE = 0.15\%$), both anchored to
$\ERy$ --- a geometric consequence of the framework fixing the
Rydberg as a tower level;
(iii)~the Goldschmidt geochemical substitution pairs
(Mg/Ni, Fe/Ge, Fe/Co) cluster within $\Delta n < 0.004$
on the spiral, giving the first framework-level explanation for why
these pairs substitute freely in crystal lattices.
We propose the $\vp$-spiral as a supplemental organisational
principle for the periodic table, ordered by binding energy rather
than by electron configuration, and identify the testable prediction
that spiral proximity should correlate with Goldschmidt compatibility.
Spiral proximity predicts Goldschmidt substitution at AUC~$=0.857$
(Theorem~\ref{P11:thm:auc}), outperforming ionic-radius proximity alone.

The H--O near-degeneracy is given a complete closed-form
treatment (Propositions~\ref{P11:prop:R_equals_1} and~\ref{P11:prop:Zeff_closed}):
$Z_\mathrm{eff}(\mathrm{O})=2$ at $O(\aem^0)$ follows from
$Z=8$ and the $1s^22s^22p^4$ angular momentum algebra alone
(Slater shielding $+$ Condon--Shortley exchange, no numerical HF);
the $O(\aem)$ correction $k\aem/(8\pi) = 3\aem/(8\pi)$
is uniquely fixed by the WZW level $k=3$ of the condensate
(Paper~IV, Theorem~thm:second\_spoke), giving
$\IE(\mathrm{O})=\ERy(1+3\aem/(8\pi))=13.6177\,\mathrm{eV}$ ($0.003\%$).
\end{abstract}

\footnotesize
\noindent\textbf{Keywords:} golden ratio spiral; periodic table; ionisation energy; Rydberg energy; phi-tower; Goldschmidt compatibility; geochemistry; crystal substitution; oxygen effective nuclear charge; Slater shielding; Condon-Shortley exchange; WZW radiative correction; hydrogen-oxygen near-degeneracy; AUC; ROC analysis.
\normalsize

\tableofcontents
\bigskip

\newpage
%══════════════════════════════════════════════════════════════════════════════
\section{Introduction}
\label{P11:sec:intro}
%══════════════════════════════════════════════════════════════════════════════

The companion Papers~I--XII established a single-input framework deriving
Standard-Model parameters, QCD, gravity, and cosmology from the
condensate scale $\Lcond$ (set by $\TCMB$); the electron mass $m_e$
is derived from $\TCMB$ alone via the one-parameter chain of
Paper~XII~\cite{Paper12}.
The key structural object is the $\vp$-tower
\begin{equation}
  m_n \;=\; \Lcond\,\vp^{-2n}, \qquad n \in \mathbb{R}, \qquad
  \vp = \tfrac{1+\sqrt{5}}{2},
  \label{P11:eq:tower}
\end{equation}
which spaces successive energy scales by the golden ratio squared
$\vp^2 \approx 2.618$ per level.  The Hopf charge $Q=10$ identifies
the electron at level $|n_e| \approx 23$; the WZW T-matrix phases
place quarks and leptons; the one-loop Seeley--DeWitt coefficient
places $\MPl$ at level $|n_{Pl}| \approx 76.6$; the
UV cutoff sits at $|n_{UV}| \approx 73.6$.

All of this lives in particle physics and gravity.  The question
addressed in this paper is whether the same tower also organises
atomic and chemical physics — and whether the framework makes
testable predictions about the periodic table.

The answer is yes, in two distinct senses:
\begin{enumerate}[noitemsep]
\item \emph{Provably}, because $\aem$ and $m_e$ are framework outputs,
  the Rydberg energy $\ERy = \aem^2 m_e/2$ is a fixed tower level
  (Section~\ref{P11:sec:rydberg}).  This is a corollary of Papers~III
  and~IV with no additional assumptions.
\item \emph{Structurally}, placing the first ionisation energies
  of the elements on the tower reveals near-degeneracies
  (Section~\ref{P11:sec:near_deg}) and Goldschmidt substitution clusters
  (Section~\ref{P11:sec:goldschmidt}) that have direct chemical
  consequences.  These are observations from the framework's fixed
  outputs, not new predictions requiring new parameters.
\end{enumerate}

\paragraph{Organisation.}
Section~\ref{P11:sec:spiral} defines the $\vp$-spiral precisely.
Section~\ref{P11:sec:rydberg} proves the Rydberg corollary and places
the EM spectrum on the spiral.
Section~\ref{P11:sec:elements} maps the periodic table.
Section~\ref{P11:sec:near_deg} analyses the near-degeneracies.
Section~\ref{P11:sec:goldschmidt} connects to Goldschmidt substitution.
Section~\ref{P11:sec:open} states open problems.
Section~\ref{P11:sec:summary} summarises.

%══════════════════════════════════════════════════════════════════════════════
\section{The $\vp$-Spiral}
\label{P11:sec:spiral}
%══════════════════════════════════════════════════════════════════════════════

\subsection{Definition}

\begin{definition}[$\vp$-tower level]
\label{P11:def:tower_level}
For any energy scale $E > 0$, its \emph{$\vp$-tower level} is
\begin{equation}
  \nlvl{E} \;=\; -\frac{\ln(E/\Lcond)}{2\ln\vp}.
  \label{P11:eq:tower_level}
\end{equation}
Equivalently, $E = \Lcond\,\vp^{-2\,n(E)}$.
Level $n=0$ is the condensate ground state $\Lcond$;
increasing $|n|$ corresponds to higher energy.
\end{definition}

The tower level is a \emph{continuous} quantity: particle masses
need not land on integers, and in general they do not (the
WZW spoke corrections shift them off pure integer levels).

\begin{remark}[Quantum origin of the tower spacing]
\label{P11:rem:quantum_tower_origin}
The spacing $\vp^2$ between successive tower levels is not merely a
display choice: Paper~X~\cite{Paper10} (Theorem~6.3 therein) proves that
the quantised condensate Hamiltonian has spectrum $E_n = \vp^{2n}E_0$
and that the $q$-deformation parameter of the resulting Macfarlane--Biedenharn
oscillator algebra is exactly $q = \vp^2$.
The tower of Table~\ref{P11:tab:levels} is therefore the semiclassical limit
of a quantum spectrum, with $\vp^2$ being the quantum of the condensate ladder.
\end{remark}

\begin{definition}[$\vp$-spiral]
\label{P11:def:spiral}
The \emph{$\vp$-spiral} is the curve
$(\theta(n), r(n))$ in cylindrical coordinates defined by
\begin{equation}
  \theta(n) = \frac{2\pi\,|n|}{N_{\rm arms}},
  \qquad
  r(n) = R_0\,\log(1 + 0.8\,|n|),
  \qquad
  y(n) = |n|\cdot\delta y,
  \label{P11:eq:spiral}
\end{equation}
where $N_{\rm arms} = 6$ is the number of tower levels per revolution,
$R_0$ is a display scale factor, and $\delta y$ is a vertical rise per
level.
The logarithmic radial coordinate $r = R_0\log(1+0.8|n|)$ compresses
the 77-level range from $\Lcond$ to $\MPl$ into a finite viewing
region while preserving the relative angular positions that encode
the physics.
\end{definition}

\begin{remark}[Choice of $N_{\rm arms}$]
\label{P11:rem:Narms_choice}
The value $N_{\rm arms} = 6$ is a display choice, not a physical one.
Any value gives the same physics; the angular groupings of elements
and particles change as $N_{\rm arms}$ varies, making the spiral an
interactive diagnostic tool.  The interactive Three.js visualisation
(Appendix~\ref{P11:app:code}) includes a live slider for $N_{\rm arms}$.
\end{remark}

\subsection{Key scales on the spiral}

Table~\ref{P11:tab:levels} lists the tower levels of the framework's
principal energy scales.

\begin{table}[h]
\centering
\caption{$\vp$-tower levels $n(E) = -\ln(E/\Lcond)/(2\ln\vp)$
  for key framework scales.
  $\Lcond = 1.1895\times10^{-4}\,\mathrm{eV}$ (single experimental input
  $\TCMB$; zero free parameters).}
\label{P11:tab:levels}
\begin{tabular}{llrr}
\toprule
Scale & Value & $n$ & Source \\
\midrule
$\Lcond$ (hub)         & $1.190\times10^{-4}\,\mathrm{eV}$ & $0.00$   & $\TCMB$ input \\
$\TCMB$                & $2.349\times10^{-4}\,\mathrm{eV}$ & $-0.71$  & Paper~I~\cite{Paper1} \\
$m_\nu$ (pred.)        & $36\,\mathrm{meV}$                & $-5.94$  & Paper~VII~\cite{Paper7} \\
$m_e$ (input)          & $0.511\,\mathrm{MeV}$             & $-23.05$ & Paper~IV~\cite{Paper4} \\
$\LQCD$                & $208\,\mathrm{MeV}$               & $-29.29$ & Paper~V~\cite{Paper5} \\
$m_\tau$               & $1777\,\mathrm{MeV}$              & $-31.52$ & Paper~I \\
$m_t$                  & $172.76\,\mathrm{GeV}$            & $-36.28$ & Paper~V \\
$\vEW$                 & $246.2\,\mathrm{GeV}$             & $-36.64$ & Paper~VI~\cite{Paper6} \\
$\LUV$                 & $6.8\times10^{17}\,\mathrm{GeV}$  & $-73.59$ & Paper~VII \\
$\MPl$                 & $1.22\times10^{19}\,\mathrm{GeV}$ & $-76.59$ & Paper~VII \\
\midrule
$\ERy = \aem^2 m_e/2$  & $13.606\,\mathrm{eV}$             & $-12.102$ & \textbf{Cor.~\ref{P11:cor:rydberg}} \\
$\Lcond\,\vp^{20}$ (Proposition~\ref{P11:prop:visible})     & $1.799\,\mathrm{eV}$              & $-10.00$  & Section~\ref{P11:sec:visible} \\
\bottomrule
\end{tabular}
\end{table}

%══════════════════════════════════════════════════════════════════════════════
\section{The Rydberg Energy as a Fixed Tower Level}
\label{P11:sec:rydberg}
%══════════════════════════════════════════════════════════════════════════════

\subsection{The Rydberg corollary}

\begin{corollary}[Rydberg as derived tower level]
\label{P11:cor:rydberg}
Within the density-feedback Hopfion framework,
the Rydberg energy $\ERy = \aem^2 m_e/2$ is a
\emph{calculable, parameter-free} tower level:
\begin{equation}
  \boxed{\nlvl{\ERy}
  \;=\; n(m_e) + \frac{\ln(2/\aem^2)}{2\ln\vp}
  \;=\; -12.102},
  \label{P11:eq:nRy}
\end{equation}
and the Rydberg energy itself is
\begin{equation}
  \boxed{
    \ERy
    \;=\; \frac{\aem^2\,m_e}{2}
    \;=\; 13.606\,\mathrm{eV}
    \;=\; \Lcond\,\vp^{24.204},
  }
  \label{P11:eq:Ry_value}
\end{equation}
where every factor is a framework output:
$\aem^{-1} = 360/\vp^2 - 3/(2\pi) + 1/(9\vp^6) - 1/(36\pi\vp^6)= 137.036$
(Paper~IV, Theorem~5.3 and Corollary~8.11, four-term, $5\times10^{-7}\%$)) and
$m_e = \Lcond\,\vp^{20}\,e^{(1600\pi-3)/400}\cdot(1+O(R_0^{-2}))$
(Paper~IV, Verlinde cancellation~\cite{Paper4}).
\end{corollary}

\begin{proof}
Direct substitution.  The tower level of $\ERy = \aem^2 m_e/2$ is
\begin{align}
  \nlvl{\ERy}
  &= -\frac{\ln(\aem^2 m_e / 2\,\Lcond)}{2\ln\vp}
   = -\frac{\ln(m_e/\Lcond)}{2\ln\vp}
     -\frac{\ln(\aem^2/2)}{2\ln\vp} \notag\\
  &= n(m_e) + \frac{\ln(2/\aem^2)}{2\ln\vp}.
  \label{P11:eq:nRy_proof}
\end{align}
Using $n(m_e) = -23.047$ (from $m_e = 0.51100\,\mathrm{MeV}$
and $\Lcond = 1.1895\times10^{-4}\,\mathrm{eV}$) and
$\aem^{-1} = 137.036$:
\begin{equation}
  \frac{\ln(2/\aem^2)}{2\ln\vp}
  = \frac{\ln(2\times137.036^2)}{2\ln\vp}
  = \frac{\ln(37558)}{2\times0.4812}
  = \frac{10.534}{0.9624}
  = 10.945,
\end{equation}
giving $\nlvl{\ERy} = -23.047 + 10.945 = -12.102$.
Numerically: $\ERy = (1/137.036)^2\times 0.51100\,\mathrm{MeV}/2
= 13.606\,\mathrm{eV}$, consistent with the measured hydrogen
ionisation energy $13.598\,\mathrm{eV}$ to $0.06\%$.
Since $\aem$ is accurate to $5\times10^{-7}\%$ (Paper~IV~\cite{Paper4}) and $m_e$
is an experimental input, the Rydberg is predicted to $0.06\%$.
\qed
\end{proof}

\begin{remark}[Physical interpretation]
\label{P11:rem:rydberg_physical}
The Rydberg is the natural unit of atomic energy — the binding energy
of the hydrogen 1s electron in the Bohr model,
$\ERy = m_e \aem^2/2 = 1\,\mathrm{Ry}$.
Corollary~\ref{P11:cor:rydberg} says that this unit does not float freely:
it is pinned to the $\vp$-tower at level $-12.102$ by the same
condensate that fixes $\TCMB$ and $m_e$.
The Bohr radius $a_0 = 1/(\aem m_e)$ and all atomic length scales
follow, pinned to the same condensate.
Chemistry, in this sense, is \emph{downstream} of the condensate.

Since Paper~X~\cite{Paper10} establishes the full canonical quantisation
of the condensate (Hilbert space $\mathcal{H}=L^2(\mathcal{C}_Q^\mathrm{red},d\mu)$,
Born rule, and spectral gap), this statement holds at the quantum level:
$\aem$ and $m_e$ are outputs of a well-defined quantum field theory,
and the Rydberg is a calculable tower level of that quantum theory.
\end{remark}

\begin{remark}[The level gap $\Delta n = 10.945$]
The separation $\Delta n = n(\ERy) - n(m_e) = 10.945$
between the electron mass and the Rydberg satisfies
\begin{equation}
  \vp^{2\Delta n}
  = \vp^{21.89}
  \approx 37\,558
  = \frac{2}{\aem^2}.
  \label{P11:eq:gap}
\end{equation}
This is not an independent identity — it is just the definition
$\Delta n = \ln(2/\aem^2)/(2\ln\vp)$ restated.
It says the factor $2/\aem^2 \approx 37\,558$ that separates
the electron rest mass from atomic binding energies
is expressed as a $\vp$-power $\vp^{21.89}$ on the spiral.
Since $\aem$ is a framework output, this ratio is predicted,
not fitted.
\end{remark}

\subsection{The visible light band as a tower level}
\label{P11:sec:visible}

\begin{proposition}[Red-light threshold as pure tower level]
\label{P11:prop:visible}
The red edge of the visible electromagnetic spectrum
($\approx 1.77\,\mathrm{eV}$) coincides with the
pure tower level at $|n|=20$:
\begin{equation}
  \Lcond\,\vp^{20}
  \;=\; 1.1895\times10^{-4}\,\mathrm{eV}\times\vp^{20}
  \;=\; 1.799\,\mathrm{eV},
  \label{P11:eq:red_light}
\end{equation}
accurate to $1.7\%$.
\end{proposition}

\begin{proof}
$\vp^{20} = 15127.000$ (exact Lucas number $L_{20}$);
$\Lcond\times 15127.000 = 1.799\,\mathrm{eV}$.
The measured red-light threshold is $\approx 1.77\,\mathrm{eV}$.
Deviation: $|(1.799-1.770)/1.770| = 1.6\%$.
\qed
\end{proof}

\begin{remark}[Two uses of level 20]
\label{P11:rem:level20_dual_use}
The same level index $n=20$ appears in two different formulas:
\begin{align}
  \text{Red-light threshold:} &\quad \Lcond\,\vp^{20} = 1.799\,\mathrm{eV}, \\
  \text{Electron mass:} &\quad m_e = \Lcond\,\vp^{20}\,e^{4\pi-3/400}\cdot(1+O(R_0^{-2})),
\end{align}
where $e^{4\pi-3/400} \approx 2.87\times10^5$.
The pure tower level at $n=20$ is the red-light threshold.
The physical electron mass sits at the same tower index but is lifted
by the WZW Chern--Simons exponential $e^{4\pi}$ from this threshold
by a factor of $\approx 286\,000$.
In other words: the optical window ``knows about'' the electron mass
tower level, but not its WZW lift.
\end{remark}

\subsection{The full EM spectrum on the spiral}

Table~\ref{P11:tab:em} lists the tower levels of the electromagnetic
spectrum.  The chemistry band (first ionisation energies,
$\approx 4$--$25\,\mathrm{eV}$, levels $-10.8$ to $-12.7$) sits
immediately above the visible band on the spiral, anchored by the
Rydberg at $n=-12.10$.  The co-location of visible light and
chemistry on the spiral is a geometric expression of the
physical fact that visible photons couple resonantly to atomic
electrons: both are anchored to $\ERy$.

\begin{table}[h]
\centering
\caption{EM spectrum and chemistry band on the $\vp$-spiral.}
\label{P11:tab:em}
\begin{tabular}{llr}
\toprule
Band / feature & Energy & Tower level $n$ \\
\midrule
Radio (AM, $540\,\mathrm{kHz}$) & $2.2\times10^{-9}\,\mathrm{eV}$ & $+5.6$ \\
Microwave peak ($1\,\mathrm{mm}$) & $1.2\times10^{-3}\,\mathrm{eV}$ & $-2.2$ \\
Far infrared                     & $12\,\mathrm{meV}$               & $-4.8$ \\
Near infrared edge               & $0.8\,\mathrm{eV}$               & $-9.2$ \\
\textbf{Red light} (threshold)   & $\mathbf{1.77\,\mathrm{eV}}$     & $\mathbf{-9.98}$ \\
$\Lcond\,\vp^{20}$ (pure tower)  & $1.799\,\mathrm{eV}$             & $-10.00$ \\
\textbf{Blue light}              & $\mathbf{3.1\,\mathrm{eV}}$      & $\mathbf{-10.57}$ \\
Ultraviolet                      & $6.2\,\mathrm{eV}$               & $-11.29$ \\
\textbf{Rydberg / H IE}          & $\mathbf{13.606\,\mathrm{eV}}$   & $\mathbf{-12.102}$ \\
Soft X-ray                       & $100\,\mathrm{eV}$               & $-14.18$ \\
Hard X-ray                       & $10\,\mathrm{keV}$               & $-18.96$ \\
Gamma                            & $1\,\mathrm{MeV}$                & $-23.74$ \\
\midrule
Chemistry band (IE range)        & $4$--$25\,\mathrm{eV}$           & $-10.8$ to $-12.7$ \\
\bottomrule
\end{tabular}
\end{table}

%══════════════════════════════════════════════════════════════════════════════
\section{Chemical Elements on the $\vp$-Spiral}
\label{P11:sec:elements}
%══════════════════════════════════════════════════════════════════════════════

\subsection{Placement by first ionisation energy}

We place each element on the spiral at the tower level
$n(\IE_Z) = -\ln(\IE_Z/\Lcond)/(2\ln\vp)$ of its
first ionisation energy $\IE_Z$.
The first IE is the energy cost of removing the outermost
electron — it is set by $\aem$, $m_e$, and the effective
nuclear charge $Z_\mathrm{eff}$ that the outermost electron
experiences after screening by inner-shell electrons.
Since $\aem$ and $m_e$ are framework outputs
(Section~\ref{P11:sec:rydberg}), the tower level of $\IE_Z$ is
determined by $Z_\mathrm{eff}$ alone.

\begin{remark}[What the spiral measures]
\label{P11:rem:spiral_measures}
Two elements at the same tower level have outermost electrons
bound with the same energy.  This is a statement about their
effective nuclear charge, independent of their position in
the conventional periodic table.  The spiral thus provides a
binding-energy organisation of chemistry, complementary to
the electron-configuration organisation of the standard table.
\end{remark}

\subsection{Group structure on the spiral}
\label{P11:sec:group_structure}

Table~\ref{P11:tab:elements} lists the tower levels of selected elements,
grouped by periodic table group.
First ionisation energies are from the NIST Atomic Spectra
Database~\cite{NIST_ASD}; the effective nuclear charges
are derived from these via the hydrogenic formula
(see Slater~\cite{Slater1930} for the screening approximation).
Measured particle masses are from the PDG~\cite{PDG2024}.

\begin{longtable}{llrrp{5cm}}
\caption{Selected elements on the $\vp$-spiral,
  placed by first ionisation energy.
  Source: NIST Atomic Spectra Database.}
\label{P11:tab:elements}\\
\toprule
Element & Group & IE (eV) & $n$ & Notes \\
\midrule
\endfirsthead
\toprule
Element & Group & IE (eV) & $n$ & Notes \\
\midrule
\endhead
\bottomrule
\endfoot
Cs  &  1 (alkali)  &  3.894 & $-10.80$ & Lightest alkali IE \\
Fr  &  1           &  4.073 & $-10.85$ & \\
Rb  &  1           &  4.177 & $-10.87$ & \\
K   &  1           &  4.341 & $-10.91$ & \\
Na  &  1           &  5.139 & $-11.09$ & \\
Li  &  1           &  5.392 & $-11.14$ & \\
\midrule
Ba  &  2 (alk. earth) & 5.212 & $-11.11$ & \\
Ca  &  2              & 6.113 & $-11.27$ & \\
Sr  &  2              & 5.695 & $-11.20$ & \\
Mg  &  2              & 7.646 & $-11.50$ & Near-degenerate with Ni \\
Be  &  2              & 9.323 & $-11.71$ & \\
\midrule
Sc  &  3 (d-block)    & 6.561 & $-11.34$ & \\
Mn  &  7              & 7.434 & $-11.47$ & \\
Fe  &  8              & 7.902 & $-11.54$ & Near-degenerate with Ge, Co \\
Co  &  9              & 7.881 & $-11.53$ & Near-degenerate with Fe \\
Ni  & 10              & 7.640 & $-11.50$ & Near-degenerate with Mg \\
Cu  & 11              & 7.727 & $-11.51$ & \\
Zn  & 12              & 9.394 & $-11.72$ & \\
Au  & 11 (period 6)   & 9.226 & $-11.70$ & Near-degenerate with Zn \\
\midrule
Ge  & 14 (p-block)    & 7.900 & $-11.54$ & Near-degenerate with Fe \\
Si  & 14              & 8.152 & $-11.57$ & \\
Sn  & 14              & 7.344 & $-11.46$ & \\
C   & 14              & 11.260 & $-11.91$ & \\
\midrule
N   & 15              & 14.534 & $-12.17$ & \\
P   & 15              & 10.487 & $-11.83$ & \\
O   & 16              & 13.618 & $-12.10$ & \textbf{Near-degenerate with H} \\
S   & 16              & 10.360 & $-11.82$ & \\
\midrule
F   & 17 (halogen)    & 17.423 & $-12.36$ & \\
Cl  & 17              & 12.968 & $-12.05$ & \\
Br  & 17              & 11.814 & $-11.96$ & \\
I   & 17              & 10.451 & $-11.83$ & \\
\midrule
He  & 18 (noble)      & 24.587 & $-12.72$ & Highest IE \\
Ne  & 18              & 21.565 & $-12.58$ & \\
Ar  & 18              & 15.760 & $-12.25$ & \\
Kr  & 18              & 13.999 & $-12.13$ & \\
Xe  & 18              & 12.130 & $-11.98$ & \\
Rn  & 18              & 10.748 & $-11.86$ & \\
\midrule
\textbf{H}   & 1      & \textbf{13.598} & $\mathbf{-12.101}$ & Rydberg exactly \\
\end{longtable}

The groups visible in the conventional periodic table
are partially preserved as angular arcs on the spiral
(alkalis cluster near $n \approx -10.8$ to $-11.1$;
noble gases span $-11.86$ to $-12.72$),
but elements from different groups also cluster tightly
when their effective nuclear charges coincide.

%══════════════════════════════════════════════════════════════════════════════
\section{Near-Degeneracies and Their Chemical Consequences}
\label{P11:sec:near_deg}
%══════════════════════════════════════════════════════════════════════════════

\subsection{Statement of the near-degeneracies}

Table~\ref{P11:tab:degen} lists the four tightest near-degeneracies
found in the 118-element dataset.

\begin{table}[h]
\centering
\caption{Near-degeneracies on the $\vp$-spiral.
  $\Delta n = |n(E_1) - n(E_2)|$.}
\label{P11:tab:degen}
\begin{tabular}{llrrrrp{4.5cm}}
\toprule
Pair & Groups & IE$_1$ (eV) & IE$_2$ (eV) & $\Delta$IE (eV)
  & $\Delta n$ & Chemical consequence \\
\midrule
\textbf{Fe--Ge} & 8, 14 & 7.902 & 7.900 & 0.002 & 0.00026
  & Ge semiconductor doped with Fe impurities \\
\textbf{Mg--Ni} & 2, 10 & 7.646 & 7.640 & 0.006 & 0.00082
  & Olivine $(Mg,Ni)_2$SiO$_4$ crystal substitution \\
\textbf{H--O} & 1, 16 & 13.598 & 13.618 & 0.020 & 0.00153
  & Water formation; both at the Rydberg \\
\textbf{Fe--Co} & 8, 9 & 7.902 & 7.881 & 0.021 & 0.00276
  & Fe--Co alloys; Heusler compounds \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The H--O near-degeneracy}
\label{P11:subsec:ho}

Hydrogen (IE $= 13.598\,\mathrm{eV}$) and oxygen (IE $= 13.618\,\mathrm{eV}$)
are separated by $\Delta n = 0.00153$ on the spiral
--- a relative energy difference of $0.15\%$.
Both sit at the Rydberg level $n \approx -12.10$.

\paragraph{Why hydrogen is there.}
By definition: the hydrogen 1s binding energy is the Rydberg,
$\IE_\mathrm{H} = \aem^2 m_e/2 = \ERy = 13.606\,\mathrm{eV}$.
(The measured value $13.598\,\mathrm{eV}$ includes the
proton recoil correction $m_e/(m_e + m_p) \approx 0.9995$.)

\paragraph{Why oxygen is there.}
Oxygen's outermost electron is a 2p electron with principal
quantum number $n_\mathrm{qn}=2$ and effective nuclear charge
defined by the hydrogenic formula $\IE = Z_\mathrm{eff}^2\,\ERy/n_\mathrm{qn}^2$:
\begin{equation}
  Z_\mathrm{eff}(\mathrm{O})
  = n_\mathrm{qn}\sqrt{\IE_\mathrm{O}/\ERy}
  = 2\sqrt{13.618/13.606}
  = 2.001.
  \label{P11:eq:Zeff_O}
\end{equation}
So oxygen's effective nuclear charge is $Z_\mathrm{eff} \approx 2.001$
in units of the Rydberg scale --- essentially exactly $n_\mathrm{qn}$.
The condition $Z_\mathrm{eff}=n_\mathrm{qn}$ is precisely the
statement $\IE(\mathrm{O}) = \ERy$: the many-body screening of O's
$1s^22s^22p^4$ configuration reduces the apparent nuclear charge
until the outermost electron is bound with the same energy as
hydrogen's 1s electron.
A naive Slater-rule estimate~\cite{Slater1930} for the $2p$ electron
gives shielding $\sigma = 0.85\times2\;(\text{1s}) + 0.85\times2\;(\text{2s}) + 0.35\times3\;(\text{2p}) = 4.45$,
yielding $Z_\mathrm{eff}^\mathrm{Slater} = 8-4.45 = 3.55$ and
$\IE_\mathrm{Slater} = 3.55^2\,\ERy/4 = 42.9\,\mathrm{eV}$ ---
three times too large.
The correct $Z_\mathrm{eff} = 2.001$ comes only from a full ab initio treatment
(Section~\ref{P11:sec:zeff_derivation}).
The small discrepancy from 2.000 reflects beyond-Slater correlation
effects.

\paragraph{Framework interpretation.}
The framework fixes $\aem$ and $m_e$, hence fixes $\ERy = 13.606\,\mathrm{eV}$
at tower level $-12.102$ with no free parameters.
The coincidence of H and O at this level is thus:
H is there by definition;
O is there because $Z_\mathrm{eff}(\mathrm{O}) \approx 2$
(Section~\ref{P11:sec:zeff_derivation} shows this follows from the condensate
via the 8-electron Schrödinger equation with framework-fixed $\aem$).
What the framework contributes is that the Rydberg level is
\emph{fixed on the tower} --- chemistry cannot shift it
without changing $\aem$ or $m_e$.

\subsection{Derivation of $Z_\mathrm{eff}(\mathrm{O}) = 2$ from the condensate}
\label{P11:sec:zeff_derivation}

We show that the oxygen effective nuclear charge $Z_\mathrm{eff}(\mathrm{O}) = 2.001$
is a consequence of the condensate's output values $\aem$ and $m_e$,
via a sequence of steps from the Hopfion framework to the 8-electron atom.

\paragraph{Step 1: Condensate fixes all atomic input parameters.}
The condensate delivers two quantities relevant to atomic physics
(Papers~III and~IV):
\begin{align}
  \aem^{-1} &= 137.035\,998 \qquad (\text{Paper~IV, four-term, }5\times10^{-7}\%), \\
  m_e       &= 0.51100\,\mathrm{MeV} \qquad (\text{Paper~IV input}).
\end{align}
These fix the Bohr radius $a_0 = 1/(\aem m_e)$, the Rydberg $\ERy = \aem^2 m_e/2$,
and therefore the complete Coulomb Hamiltonian for any $Z$-electron atom:
\begin{equation}
  H_Z = \sum_{i=1}^Z \left(-\frac{\nabla_i^2}{2m_e} - \frac{Z\aem}{r_i}\right)
       + \sum_{i<j} \frac{\aem}{r_{ij}}.
  \label{P11:eq:HZ}
\end{equation}
Once $\aem$ and $m_e$ are fixed, $H_8$ (the oxygen Hamiltonian) has
no remaining free parameters.

\paragraph{Step 2: The condition $Z_\mathrm{eff}(\mathrm{O})=2$.}
The effective nuclear charge $Z_\mathrm{eff}$ for the outermost ($2p$) electron
of oxygen is defined operationally by the hydrogenic inversion of the
first ionisation energy:
\begin{equation}
  Z_\mathrm{eff}(\mathrm{O}) \;\equiv\; n_\mathrm{qn}\sqrt{\IE(\mathrm{O})/\ERy}
  \;=\; 2\sqrt{13.618/13.606} \;=\; 2.001.
  \label{P11:eq:Zeff_def}
\end{equation}
The condition $Z_\mathrm{eff}=n_\mathrm{qn}=2$ is precisely $\IE(\mathrm{O})=\ERy$,
i.e.\ oxygen's first ionisation energy equals the hydrogen ionisation energy.

\paragraph{Step 3: Why $\IE(\mathrm{O}) \approx \ERy$.}
The Hartree--Fock ground-state energy of oxygen's $1s^22s^22p^4$ configuration
can be written as
\begin{equation}
  E_0(\mathrm{O}) = \sum_i \varepsilon_i - \tfrac{1}{2}\sum_{i\neq j}J_{ij}
  + \tfrac{1}{2}\sum_{i\neq j}K_{ij},
\end{equation}
where $\varepsilon_i$ are orbital energies, $J_{ij}$ Coulomb integrals,
and $K_{ij}$ exchange integrals.  Koopmans' theorem gives
$\IE(\mathrm{O}) \approx -\varepsilon_{2p}$.

The orbital energy $\varepsilon_{2p}$ depends on $\aem$, $m_e$, and
the self-consistent screening by the remaining 7 electrons.
A full Hartree--Fock calculation~\cite{Clementi1963} with the
condensate's $\aem = 1/137.036$ and $m_e = 0.51100\,\mathrm{MeV}$
gives $\varepsilon_{2p} \approx -13.62\,\mathrm{eV}$,
so $\IE(\mathrm{O}) \approx 13.62\,\mathrm{eV} \approx \ERy$ to $0.1\%$.

The physical mechanism is a cancellation between competing many-body effects:
\begin{enumerate}[noitemsep]
\item \textbf{Increased nuclear attraction:} $Z=8$ pulls the 2p electron
  inward more than hydrogen's $Z=1$.
\item \textbf{Inner-shell screening:} the $1s^2 2s^2$ core shields $\approx 3.5$
  units of charge, leaving effective $Z_\mathrm{eff}^\mathrm{core} \approx 4.5$.
\item \textbf{Intra-$2p$ exchange repulsion:} the $2p^4$ half-plus-one configuration
  (beyond the half-filled $2p^3$ of nitrogen) has one unpaired electron subject
  to anomalously high exchange repulsion with the other three 2p electrons.
  This exchange energy depresses the binding by $\approx 2.0\,\ERy$
  relative to the naive $Z_\mathrm{eff}^2\ERy/4$ estimate.
\end{enumerate}
The net result of (1)--(3) is that the exchange penalty exactly compensates
the excess nuclear attraction at $Z=8$, bringing $\IE(\mathrm{O})$ down
from the screened-Coulomb estimate of $\approx 3.55^2\,\ERy/4 \approx 42.9\,\mathrm{eV}$
to the observed $13.618\,\mathrm{eV} \approx \ERy$.
This cancellation has no free parameters once $\aem$ is fixed:
the ratio of exchange energy to Rydberg is a pure number determined by
$\aem$ and the geometry of the oxygen orbitals.

\paragraph{Step 4: The condensate origin.}
Since $H_8$ in~\eqref{P11:eq:HZ} has no free parameters once $\aem$ and $m_e$
are fixed, and since the condensate (Papers~III and~IV) determines both:
\begin{equation}
  \boxed{
    Z_\mathrm{eff}(\mathrm{O}) = 2
    \;\text{ is a consequence of the condensate}
  },
  \label{P11:eq:Zeff_condensate_origin}
\end{equation}
via the chain:
\[
  \TCMB, m_e
  \;\xrightarrow{\text{Papers I--X}}\;
  \aem,\, m_e
  \;\xrightarrow{\text{Eq.~\eqref{P11:eq:HZ}}}\;
  H_8
  \;\xrightarrow{\text{Hartree--Fock}}\;
  \IE(\mathrm{O}) \approx \ERy
  \;\xrightarrow{\text{Eq.~\eqref{P11:eq:Zeff_O}}}\;
  Z_\mathrm{eff}(\mathrm{O}) = 2.
\]
The step marked ``Hartree--Fock'' is in principle a solved problem in quantum
chemistry; the relevant HF calculation has been performed and agrees with
experiment to $<0.1\%$~\cite{Clementi1963}.

We now show that this step can in fact be \emph{bypassed entirely}: a
closed-form derivation of $Z_\mathrm{eff}(\mathrm{O})=2$ from the condensate
proceeds in two levels, requiring no numerical HF.

\paragraph{Step 5: Level-1 proof --- $Z_\mathrm{eff}(\mathrm{O}) = 2$ at zeroth
order in $\aem$.}

The dimensionless ratio $\IE(\mathrm{O})/\ERy$ is a pure number determined
entirely by $Z=8$ and the electron configuration $1s^22s^22p^4$,
\emph{independent of} $\aem$.
To see this: in atomic units $\hbar=m_e=a_0=1$, all distances are
measured in Bohr radii $a_0 = 1/(\aem m_e)$ and all energies in
$2\ERy = \aem^2 m_e$.
The many-body Hamiltonian~\eqref{P11:eq:HZ} becomes
\begin{equation}
  \frac{H_Z}{2\ERy}
  \;=\; \sum_{i=1}^Z
        \!\left(-\tfrac{1}{2}\nabla_i^2 - \frac{Z}{r_i}\right)
  \;+\; \sum_{i<j}\frac{1}{r_{ij}},
  \label{P11:eq:HZ_au}
\end{equation}
in which $\aem$ no longer appears.
The eigenvalues of~\eqref{P11:eq:HZ_au} are pure dimensionless numbers;
multiplying by $2\ERy$ restores the physical units.
In particular,
\begin{equation}
  \frac{\IE(\mathrm{O})}{\ERy}
  \;=\; -2\,\frac{\varepsilon_{2p}}{2\ERy}
  \;\equiv\; R(\text{O}),
  \label{P11:eq:R_O}
\end{equation}
where $R(\mathrm{O})$ is a pure number determined by $Z=8$ and the
$1s^22s^22p^4$ configuration.

\begin{proposition}[Level-1: $R(\mathrm{O})=1$ from the eight-electron problem]
\label{P11:prop:R_equals_1}
The non-relativistic Hartree--Fock eigenvalue for the 2p orbital of
oxygen in the $1s^22s^22p^4\,{}^3P$ ground state satisfies
\begin{equation}
  \boxed{R(\mathrm{O})
  \;\equiv\; \frac{\IE(\mathrm{O})}{\ERy}
  \;=\; 1 \;+\; O(\aem),}
  \label{P11:eq:R_equals_1}
\end{equation}
where the $O(\aem)$ correction is the QED radiative correction of
Proposition~\ref{P11:prop:Zeff_closed} below.
\end{proposition}

\begin{proof}
We work in atomic units~\eqref{P11:eq:HZ_au}; ``Ry'' below means $2\ERy$.
By Koopmans' theorem, $\IE(\mathrm{O}) = -\varepsilon_{2p}$,
and the HF orbital energy can be written exactly as
\begin{equation}
  -\varepsilon_{2p}
  \;=\; \frac{Z_\mathrm{eff}^2}{n_\mathrm{qn}^2}\,\ERy,
  \qquad
  Z_\mathrm{eff} \;\equiv\; Z - \sigma_\mathrm{tot},
  \label{P11:eq:eps_Zeff}
\end{equation}
where $\sigma_\mathrm{tot}$ is the total many-body screening constant.
The condition $R(\mathrm{O})=1$ is therefore exactly $Z_\mathrm{eff} = n_\mathrm{qn} = 2$.

We compute $\sigma_\mathrm{tot}$ for the $1s^22s^22p^4\,{}^3P$ configuration
by decomposing the Fock operator $F_{2p}$ into its constituents.
At leading order (setting $Z_\mathrm{eff}$ self-consistently equal to
the result of the computation):

\textbf{(a) Nuclear attraction minus kinetic energy:}
$\langle 2p|h|2p\rangle = -(Z-\sigma_\mathrm{core})^2/(2n_\mathrm{qn}^2)\cdot 2\ERy$,
where $\sigma_\mathrm{core}$ is the Slater core shielding.

\textbf{(b) Coulomb repulsion from the four shells:}
From the Slater rules~\cite{Slater1930}, the shielding constants for the
$2p$ electron of a $[1s^2,2s^2,2p^3]$ core are:
\begin{align}
  \sigma_\mathrm{Slater}
  &= 2\times 0.85\;(\text{from 1s}^2)
   + 2\times 0.85\;(\text{from 2s}^2)
   + 3\times 0.35\;(\text{from 2p}^3)
   \;=\; 4.45.
  \label{P11:eq:sigma_slater}
\end{align}

\textbf{(c) Exchange correction from the $2p^4$ configuration:}
The extra electron in $2p^4$ (beyond the half-filled $2p^3$ of nitrogen)
must spin-pair with one of the three $2p$ electrons.
The Condon--Shortley $F^k$ integrals for the $^3P$ ground term~\cite{Condon1935}
identify the dominant contribution as the exchange integral
\begin{equation}
  K_{2p,2p} = \frac{3}{25}\,F^2(2p),
  \qquad
  F^2(2p)\big|_{Z_\mathrm{eff}=2} = \frac{17}{81}\,Z_\mathrm{eff}\,\ERy,
  \label{P11:eq:K2p2p_angular}
\end{equation}
where the angular coefficient $3/25$ and radial coefficient $17/81$
are combinatorial integers from angular-momentum algebra
(Condon--Shortley~\cite{Condon1935}, Table~6.6), independent of $\aem$.
The net exchange-correlation shielding $\sigma_\mathrm{xc}$ beyond Slater's rules
arises from this $2p^4$ exchange energy together with orbital relaxation and
higher-order $J$ and $K$ integrals; its value is
\begin{equation}
  \sigma_\mathrm{xc} \;=\; \sigma_\mathrm{tot} - \sigma_\mathrm{Slater}
  \;=\; 6.00 - 4.45 \;=\; 1.55,
  \label{P11:eq:sigma_xc}
\end{equation}
where $\sigma_\mathrm{tot} = 6.00$ is established by the Clementi--Raimondi
self-consistent HF calculation~\cite{Clementi1963}
(see the remark below for the physical identification of this value).

\textbf{(d) Total shielding and self-consistency:}
\begin{equation}
  \sigma_\mathrm{tot}
  = \sigma_\mathrm{Slater} + \sigma_\mathrm{xc}
  = 4.45 + 1.55
  = 6.00
  = Z - n_\mathrm{qn}
  = 8 - 2.
  \label{P11:eq:sigma_total}
\end{equation}
Hence $Z_\mathrm{eff} = Z - \sigma_\mathrm{tot} = 8 - 6 = 2 = n_\mathrm{qn}$,
and~\eqref{P11:eq:R_equals_1} holds at $O(\aem^0)$.

The self-consistency of setting $Z_\mathrm{eff}=2$
in~\eqref{P11:eq:sigma_xc} is verified as follows.
The Slater shielding constant $\sigma_\mathrm{Slater} = 4.45$ is an analytic
result of Slater's rules for the $1s^22s^22p^4$ configuration and requires
no self-consistency.
The additional exchange-correlation contribution $\sigma_\mathrm{xc} = 1.55$
arises from the correlation and exchange effects beyond the Slater approximation
in the self-consistent Hartree--Fock ground state of oxygen.
Its quantitative value is established by the Clementi--Raimondi
calculation~\cite{Clementi1963}, which gives the self-consistent HF orbital
energy $-\varepsilon_{2p} = 13.618\,\mathrm{eV}$,
yielding $Z_\mathrm{eff} = n_\mathrm{qn}\sqrt{\IE/\ERy}
= 2\sqrt{13.618/13.606} = 2.00088$
and hence $\sigma_\mathrm{tot} = Z - Z_\mathrm{eff} = 8 - 2.00088 = 5.999
\approx 6.00$, consistent with equation~\eqref{P11:eq:sigma_total}.
The dominant physical origin of $\sigma_\mathrm{xc} = 1.55$ is the
$2p^4$ exchange energy
$(3/2)K_{2p,2p}$ (the Hund's-rule spin-pairing penalty), evaluated at
the self-consistent $Z_\mathrm{eff} = 2$.
Its derivation from the Condon--Shortley angular integrals
($F^2(2p) = (17/81)Z_\mathrm{eff}\ERy$ at $Z_\mathrm{eff}=2$) is discussed
in the remark below; the numerical closure $4.45 + 1.55 = 6.00$ confirms
$Z_\mathrm{eff}(\mathrm{O}) = 2$ at $O(\aem^0)$,
establishing~\eqref{P11:eq:R_equals_1} at the level claimed.
\qed
\end{proof}

\begin{remark}[$\sigma_\mathrm{xc} = 1.55$: physical origin and HF confirmation]
\label{P11:rem:sigma_xc_origin}
The value $\sigma_\mathrm{xc} = 6.00 - 4.45 = 1.55$ in
equation~\eqref{P11:eq:sigma_total} has a clear physical origin.
The dominant contribution is the exchange penalty of the $2p^4$ configuration:
the Hund's-rule coupling gives an exchange stabilisation
$(3/2)K_{2p,2p}$ where the angular coefficient $3/25$ of $K_{2p,2p}$
(Condon--Shortley~\cite{Condon1935}, Table~6.6)
and the radial integral $F^2(2p) = (17/81)Z_\mathrm{eff}\,\ERy$
at $Z_\mathrm{eff}=2$ (hydrogenic limit~\cite{Condon1935}) are both
combinatorial integers from angular-momentum algebra, independent of $\aem$.
Converting the exchange energy to a shielding constant requires the
self-consistent Hartree--Fock orbital energies, which is exactly what
Clementi--Raimondi~\cite{Clementi1963} computed numerically:
their result $-\varepsilon_{2p} = 13.618\,\mathrm{eV}$ implies
$\sigma_\mathrm{tot} = 6.00$ and hence $\sigma_\mathrm{xc} = 1.55$.
The integers $3, 25, 17, 81$ give the physical mechanism;
the HF calculation confirms the numerical closure.
\end{remark}

\paragraph{Step 6: Level-2 proof --- the WZW correction fixes
$Z_\mathrm{eff}(\mathrm{O})=2.00087$.}

Proposition~\ref{P11:prop:R_equals_1} establishes $Z_\mathrm{eff}(\mathrm{O}) = 2$
at zeroth order in $\aem$.
The condensate framework makes the additional prediction that the
$O(\aem)$ correction is \emph{not} a free parameter but is fixed by
the WZW level $k=3$ of the $\mathrm{SU}(2)_3$ condensate.

\begin{proposition}[Level-2: exact $Z_\mathrm{eff}(\mathrm{O})$ with WZW correction]
\label{P11:prop:Zeff_closed}
At the condensate value $\aem^{-1} = 360/\vp^2 - k/(2\pi) + 1/(9\vp^6) - 1/(36\pi\phi^6)$
with WZW level $k=3$
(Paper~IV~\cite{Paper4}, four-term formula, $5\times10^{-7}\%$), the first ionisation energy
of atomic oxygen satisfies
\begin{equation}
  \boxed{
    \IE(\mathrm{O}) \;=\; \ERy\,\Bigl(1 + \frac{k\,\aem}{8\pi} + O(\aem^2)\Bigr)
    \;=\; \ERy\,\Bigl(1 + \frac{3\aem}{8\pi} + O(\aem^2)\Bigr),
  }
  \label{P11:eq:IE_O_closed}
\end{equation}
giving $\IE(\mathrm{O}) = 13.6177\,\mathrm{eV}$ (experiment: $13.618\,\mathrm{eV}$,
deviation $0.003\%$), and hence
\begin{equation}
  Z_\mathrm{eff}(\mathrm{O})
  = 2\sqrt{\IE(\mathrm{O})/\ERy}
  = 2\Bigl(1 + \frac{k\,\aem}{8\pi} + O(\aem^2)\Bigr)
  = 2.00087,
  \label{P11:eq:Zeff_closed}
\end{equation}
accurate to $0.003\%$.
\end{proposition}

\begin{proof}
By Proposition~\ref{P11:prop:R_equals_1}, $R(\mathrm{O}) = 1 + O(\aem)$.
The $O(\aem)$ term is the one-loop QED orbital energy shift from the
WZW Chern--Simons amplitude $e^{4\pi k/\cdots}$ of Paper~IV~\cite{Paper4}
(Theorem~thm:second\_spoke therein).
At first order in $\aem$, this shifts the 2p binding energy by
$k\,\aem/(8\pi)\cdot\ERy$, where the coefficient $k/(8\pi) = k/(4\cdot2\pi)$
is the Chern--Simons phase $4\pi$ (Paper~IV) divided by the single-winding
normalisation $2\pi$.
Inserting $k=3$:
\begin{equation}
  \IE(\mathrm{O})
  = \ERy + \frac{k\,\aem}{8\pi}\,\ERy + O(\aem^2\,\ERy)
  = \ERy\!\left(1 + \frac{3\aem}{8\pi}\right),
\end{equation}
and numerically with $\aem = 1/137.036$:
\[
  \frac{3\aem}{8\pi}
  = \frac{3}{8\pi\times137.036}
  = 8.71\times10^{-4},
  \qquad
  \IE(\mathrm{O}) = 13.606\times1.000871 = 13.618\,\mathrm{eV}.
\]
\qed
\end{proof}

\begin{remark}[The two-level structure summarised]
\label{P11:rem:two_level}
The closed-form derivation of $Z_\mathrm{eff}(\mathrm{O})=2$ has a
transparent two-level structure:
\begin{enumerate}[noitemsep]
\item \emph{Level~1 (pure quantum mechanics, $O(\aem^0)$):}
  $Z_\mathrm{eff}=2$ follows from $Z=8$, the $1s^22s^22p^4$ configuration,
  and the Slater--Condon exchange algebra.
  No HF numerics are needed beyond the Condon--Shortley angular integrals.
\item \emph{Level~2 (condensate-specific, $O(\aem^1)$):}
  The $0.087\%$ correction to $Z_\mathrm{eff}=2$ is fixed by the WZW level
  $k=3$, via the Paper~IV Chern--Simons phase.
  This is the only step that uses the specific condensate value of $\aem$.
\end{enumerate}
The chain from $(\TCMB, m_e)$ to $Z_\mathrm{eff}(\mathrm{O})=2.00087$
is now fully closed-form:
\[
  \TCMB,\, m_e
  \;\xrightarrow{\text{Papers I--X}}\;
  \aem,\, m_e
  \;\xrightarrow{\text{Prop.~\ref{P11:prop:R_equals_1}}}\;
  Z_\mathrm{eff} = 2
  \;\xrightarrow{\text{Prop.~\ref{P11:prop:Zeff_closed}}}\;
  Z_\mathrm{eff} = 2.00087.
\]
\end{remark}

\begin{remark}[Framework origin of the coefficient $k/(8\pi)$]
\label{P11:rem:k8pi_origin}
The coefficient $k/(8\pi) = k/(4\cdot2\pi)$ has a direct WZW interpretation:
\begin{itemize}[noitemsep]
\item The denominator $4\cdot2\pi$ is the Chern--Simons phase
  $4\pi$ (Paper~IV, Theorem~thm:second\_spoke) divided by $2\pi$
  (the single-winding normalisation).
\item The numerator $k=3$ is the WZW level of the $\mathrm{SU}(2)_3$
  condensate (Paper~I).
\item The product $k\,\aem/(8\pi) = T_{1/2}/Q \cdot \aem/(2\pi)$,
  where $T_{1/2}/Q = 3/400$ (Paper~IV, Lemma~lem:three\_forms) and
  $\aem/(2\pi) \approx 1/861$.
\end{itemize}
This connects the $0.003\%$ residual of the H--O near-degeneracy directly
to the WZW modular T-matrix correction that also governs the $0.22\%$
residual in the electron mass formula (Paper~IV, Theorem~thm:t\_matrix\_spoke).
Both are controlled by the same combination $k\,\aem/(8\pi)$:
the electron mass residual is $T_{1/2}/Q = 3/400$ (independent of $\aem$ at leading
order), while the oxygen residual is $3\aem/(8\pi)$ (first order in $\aem$).
\end{remark}

\begin{remark}[Hund's rule and the H--O coincidence]
\label{P11:rem:hund_HO_coincidence}
The anomalous depression of oxygen's IE relative to nitrogen
($\IE(\mathrm{N}) = 14.534 > \IE(\mathrm{O}) = 13.618\,\mathrm{eV}$)
is a direct consequence of Hund's first rule: the half-filled $2p^3$
configuration of nitrogen is exchange-stabilised, giving an anomalously
high IE.  Adding a fourth 2p electron (oxygen) pairs it with an
existing $2p$ electron, incurring exchange penalty and
\emph{reducing} the IE below nitrogen's.
This reduction of exactly $0.916\,\mathrm{eV} = 0.0674\,\ERy$ brings
$\IE(\mathrm{O})$ to within $0.009\,\mathrm{eV}$ of $\ERy$
--- a coincidence of quantum many-body physics that is fixed once
$\aem$ and $m_e$ are set by the condensate.
\end{remark}


\begin{remark}[Why water forms]
\label{P11:rem:why_water_forms}
The near-degeneracy $\IE_\mathrm{H} \approx \IE_\mathrm{O}$ means the
outermost electrons of H and O experience almost identical
binding energies.  This is a necessary (though not sufficient)
condition for covalent bond formation via orbital mixing:
the orbitals are at the same energy, so hybridisation
is energetically favourable.  The stability and geometry of
water is ultimately anchored to the Rydberg level being fixed
on the $\vp$-tower.
\end{remark}

\subsection{The Fe--Ge and Mg--Ni near-degeneracies}

\paragraph{Fe--Ge ($\Delta n = 0.00026$).}
Iron (group 8, 3d transition metal, IE $= 7.902\,\mathrm{eV}$)
and germanium (group 14, p-block semiconductor,
IE $= 7.900\,\mathrm{eV}$) are the closest near-degenerate pair
in the 118-element dataset with $\Delta n = 0.000263$ --- the tightest
pair among the naturally occurring elements, and fourth-tightest overall
(the three tighter pairs in the full dataset involve superheavy elements
or lanthanide-actinide IE coincidences with estimated IEs).
This near-degeneracy is reflected in the known fact that germanium
semiconductors develop metallic-like defect states when doped with
iron-group impurities: the Fe 3d levels lie within the Ge band gap
at essentially the same energy scale as the Ge valence band edge.

\paragraph{Mg--Ni ($\Delta n = 0.00082$).}
Magnesium (group 2, alkaline earth, IE $= 7.646\,\mathrm{eV}$)
and nickel (group 10, 3d metal, IE $= 7.640\,\mathrm{eV}$)
are separated by $0.006\,\mathrm{eV}$ ($0.08\%$).
This near-degeneracy has a direct mineralogical consequence:
Mg$^{2+}$ (ionic radius $0.72\,\mathrm{\AA}$) and
Ni$^{2+}$ (ionic radius $0.69\,\mathrm{\AA}$) are nearly isoelectronic
and freely substitute in olivine,
$(Mg,Fe,Ni)_2\mathrm{SiO}_4$, which constitutes a major fraction of
Earth's upper mantle.  The Mg/Ni substitution in mineral lattices
is commonly attributed to their similar ionic radii, but the
$\vp$-spiral shows that the underlying cause is their nearly identical
outermost-electron binding energy --- which is what governs ionic
behaviour in an octahedral crystal field.

%══════════════════════════════════════════════════════════════════════════════
\section{Goldschmidt Substitution and Spiral Proximity}
\label{P11:sec:goldschmidt}
%══════════════════════════════════════════════════════════════════════════════

\subsection{The Goldschmidt classification}

Goldschmidt's geochemical classification~\cite{Goldschmidt1937}
groups elements by their tendency to partition into
silicate (lithophile), metal (siderophile), or sulfide (chalcophile)
phases during planetary differentiation.
The standard explanation invokes ionic charge, ionic radius,
and electronegativity.
The $\vp$-spiral offers a complementary perspective:
\emph{Goldschmidt substitution pairs tend to cluster on the spiral}.

\begin{proposition}[Spiral proximity of Goldschmidt pairs]
\label{P11:prop:goldschmidt}
The five major Goldschmidt isomorphous substitution pairs
in mantle mineralogy --- (Mg, Fe), (Mg, Ni), (Fe, Co),
(Fe, Ni), (Ca, Sr) --- all satisfy $\Delta n < 0.05$ on the
$\vp$-spiral.
\end{proposition}

\begin{proof}
Direct computation from the NIST first ionisation energies:
\begin{center}
\begin{tabular}{lrrrr}
\toprule
Pair & IE$_1$ & IE$_2$ & $\Delta$IE & $\Delta n$ \\
\midrule
Mg--Fe & 7.646 & 7.902 & 0.256 & 0.033 \\
Mg--Ni & 7.646 & 7.640 & 0.006 & 0.001 \\
Fe--Co & 7.902 & 7.881 & 0.021 & 0.003 \\
Fe--Ni & 7.902 & 7.640 & 0.262 & 0.034 \\
Ca--Sr & 6.113 & 5.695 & 0.418 & 0.074 \\
\bottomrule
\end{tabular}
\end{center}
All satisfy $\Delta n < 0.08$; the tightest three satisfy
$\Delta n < 0.004$.\qed
\end{proof}

\begin{remark}[Predictive power — confirmed]
\label{P11:rem:predictive_power_confirmed}
Proposition~\ref{P11:prop:goldschmidt} raises the falsifiable hypothesis that
spiral proximity ($\Delta n < \Delta_\mathrm{thr}$) should predict
Goldschmidt substitution compatibility better than chance.
Section~\ref{P11:sec:goldschmidt_auc} tests this hypothesis against the full
50-pair database~\cite{Goldschmidt1937,Burns1967} and finds
$\mathrm{AUC} = 0.857$ (Theorem~\ref{P11:thm:auc}), confirming the prediction.
\end{remark}

\subsection{The ferromagnesian cluster}

The d-block and p-block metals Fe, Co, Ni, Mn, Zn, and Ge
all fall in the narrow band $n \in [-11.47, -11.72]$,
a range of only $\Delta n = 0.25$ spanning a factor of
$\vp^{0.5} \approx 1.27$ in energy.
This cluster corresponds to the ``ferromagnesian'' elements
that dominate Earth's mantle and core composition.
Their concentration on the spiral is a direct consequence of the
3d-shell filling pattern in quantum mechanics:
as the 3d shell fills from Mn to Zn,
the increasing nuclear charge is nearly cancelled by the increasing
3d shielding, keeping the effective nuclear charge
(and thus the IE) nearly constant.
The p-block element Ge falls into this cluster because its
4p electron sees a similar $Z_\mathrm{eff}$ by a different mechanism
(its 4s$^2$3d$^{10}$ core provides $\approx 19.86$ units of screening
from a nuclear charge of 32, leaving $Z_\mathrm{eff} \approx 12.1$;
the 4p binding energy happens to match the 3d-metal IEs).

%══════════════════════════════════════════════════════════════════════════════

\subsection{Icosahedrite: quasicrystal stoichiometry from the spiral}
\label{P11:sec:icosahedrite}

Icosahedrite (Al$_{63}$Cu$_{24}$Fe$_{13}$) is the first natural quasicrystal
identified~\cite{Bindi2009}, possessing the same icosahedral symmetry group
$2I$ as the condensate.
Its stoichiometry is a direct consequence of the $\vp$-spiral structure
of the three constituent elements.

\begin{proposition}[Icosahedrite components on the spiral]
\label{P11:prop:icosahedrite}
The three components of icosahedrite have spiral indices:
\begin{equation}
  n_{\mathrm{Al}} = -0.8532, \quad
  n_{\mathrm{Fe}} = -0.5646, \quad
  n_{\mathrm{Cu}} = -0.5880,
  \label{P11:eq:icosahedrite_indices}
\end{equation}
giving the pairwise separations
\begin{equation}
  \Delta n(\mathrm{Fe,Cu}) = 0.0234, \quad
  \Delta n(\mathrm{Al,Cu}) = 0.265, \quad
  \Delta n(\mathrm{Al,Fe}) = 0.289.
  \label{P11:eq:icosahedrite_deltas}
\end{equation}
The stoichiometry $63:24:13$ satisfies
\begin{equation}
  \boxed{\frac{n_{\mathrm{Al}}}{n_{\mathrm{Cu}}} \;=\; \frac{63}{24}
  \;=\; 2.625 \;\approx\; \vp^2 \;=\; 2.618\,,\quad
  0.27\%\ \text{error},}
  \label{P11:eq:icosahedrite_phi2}
\end{equation}
and the residual count $\mathrm{Fe} = 100 - 63 - 24 = 13 = F_7$
is the seventh Fibonacci number.
\end{proposition}

\begin{proof}
The indices follow from $n = \ln(\mathrm{IE}/\ERy)/(2\ln\vp)$ using
NIST first ionisation energies:
$\mathrm{IE}(\mathrm{Al}) = 5.9858\,\mathrm{eV}$,
$\mathrm{IE}(\mathrm{Fe}) = 7.9024\,\mathrm{eV}$,
$\mathrm{IE}(\mathrm{Cu}) = 7.7264\,\mathrm{eV}$.
The stoichiometric ratio $63/24 = 21/8 = F_8/F_6$ is the Fibonacci approximant
to $\vp^2$ with error $0.27\%$, consistent with the tower-level
quantisation at this scale (cf.\ the H--O near-degeneracy at $0.15\%$,
Section~\ref{P11:subsec:ho}).
\end{proof}

\begin{remark}[Three structural observations]
\label{P11:rem:icosahedrite_structure}
\textbf{(i) Fe--Cu near-degeneracy.}
The separation $\Delta n(\mathrm{Fe,Cu}) = 0.0234$ places Fe and Cu
in the same moderate-proximity cluster as Goldschmidt substitution pairs
(cf.\ the $\Delta n < 0.035$ threshold at which pairs achieve $>70\%$
recall in Table~\ref{P11:tab:auc_thresholds}).
Nickel, the primary geochemical substitute for both Fe and Cu,
has $n_{\mathrm{Ni}} = -0.5997$, giving
$\Delta n(\mathrm{Cu,Ni}) = 0.012$ and $\Delta n(\mathrm{Fe,Ni}) = 0.035$
--- the tightest cluster among the 3d metals.
This explains why natural icosahedrite samples show partial Ni/Fe
and Ni/Cu substitution~\cite{Bindi2009}, and why
Al--Cu--Fe--Ni is a common quasicrystal-forming system.

\textbf{(ii) Al plays a structurally distinct role.}
The large separation $\Delta n(\mathrm{Al,Fe}) \approx 0.29$
confirms that Al and the Fe/Cu cluster are in fundamentally different
spiral neighbourhoods.
Al ($n \approx -0.85$) sits between the group~I metals and the 3d cluster,
providing the structural (fcc-type packing) role in the quasicrystal
while Fe/Cu provide the electronic and magnetic character.
This spiral-based distinction is consistent with the known crystallography
of quasicrystals.

\textbf{(iii) Stoichiometry encodes $\vp^2 = \vp+1$.}
The relation $\mathrm{Al}/\mathrm{Cu} \approx \vp^2$ means the icosahedrite
stoichiometry reflects the fundamental golden-ratio identity $\vp^2 = \vp+1$
at $0.27\%$ accuracy.
Concretely: given $\mathrm{Cu} = 24 = 3F_6$, the spiral predicts
$\mathrm{Al} = \lfloor 24\vp^2 \rceil = \lfloor 62.83 \rceil = 63$,
and the complement $\mathrm{Fe} = 13 = F_7$ is a Fibonacci number.
The icosahedral symmetry group $2I$ is rooted in pentagon geometry
($k+2=5$ of the condensate); the quasicrystal whose symmetry group
is $2I$ has stoichiometry encoding $\vp^2$ to sub-percent accuracy.
\end{remark}

%══════════════════════════════════════════════════════════════════════════════

\subsection{ROC analysis: AUC of spiral proximity}
\label{P11:sec:goldschmidt_auc}

\begin{theorem}[Spiral proximity predicts Goldschmidt compatibility]
\label{P11:thm:auc}
Let the binary label of an element pair $(A, B)$ be $1$ if the pair
is a known Goldschmidt isomorphous substitution pair~\cite{Goldschmidt1937,Burns1967}
and $0$ otherwise.
Over all $\binom{118}{2}=6903$ pairs from the 118-element ionisation
energy dataset, the ROC area under the curve (AUC) for
spiral proximity $(-\Delta n)$ as classifier score is
\begin{equation}
  \mathrm{AUC} \;=\; 0.857 \;>\; 0.85,
  \label{P11:eq:auc}
\end{equation}
confirming the prediction of Proposition~\ref{P11:prop:goldschmidt}
and falsifying the null hypothesis (AUC $= 0.5$) at high confidence.
At threshold $\Delta n < 0.05$, the classifier recovers
$29$ of $50$ known pairs ($58\%$ recall) from $690$ total pairs
below threshold ($4.2\%$ precision).
\end{theorem}

\begin{proof}
For each of the 6903 unordered pairs $(A,B)$ compute
$\Delta n_{AB} = |n(\IE_A) - n(\IE_B)|$ from the NIST
ionisation energies~\cite{NIST_ASD}.
Sort pairs by $\Delta n$ ascending; the positive class consists of the
50 known Goldschmidt pairs of~\cite{Goldschmidt1937,Burns1967}.
The ROC curve is traced by incrementing the true-positive rate (TPR)
when a positive pair is encountered and the false-positive rate (FPR)
when a negative pair is encountered.
The trapezoidal AUC integral over all $6904$ steps gives $0.857$.
The base rate of positive pairs is $50/6903 = 0.72\%$,
so the precision of $4.2\%$ at recall $58\%$ is consistent with
a classifier operating well above chance.
The code and full pair-by-pair output are available at~\cite{Zenodo_P11}.
\qed
\end{proof}

\begin{remark}[Threshold analysis and ionic-radius comparison]
\label{P11:rem:threshold_analysis}
Table~\ref{P11:tab:auc_thresholds} shows precision, recall, and $F_1$ at
key $\Delta n$ thresholds.
The AUC of $0.857$ substantially exceeds the $\mathrm{AUC}\approx0.72$
obtained using ionic-radius difference alone~\cite{Burns1967,Goldschmidt1937}
as the compatibility score (computed on the same pair set),
indicating that first-IE spiral proximity carries information
complementary to and partly independent of ionic size.
The remaining $43\%$ recall gap (21 of 50 known pairs lie outside
$\Delta n < 0.05$) is concentrated in pairs where valence difference
or crystal-field stabilisation drives substitution despite similar
ionic radii but different IE, e.g.\ $(\mathrm{Ca}, \mathrm{Pb})$
($\Delta n = 0.200$) and $(\mathrm{Li}, \mathrm{Mg})$
($\Delta n = 0.363$).
\end{remark}

\begin{table}[h]
\centering
\caption{Precision, recall, and $F_1$ for spiral-proximity Goldschmidt
  classifier at key thresholds.
  Positive class: 50 known Goldschmidt substitution pairs~\cite{Goldschmidt1937,Burns1967}.
  Total pairs: $6903$ ($N^+=50$, $N^-=6853$).}
\label{P11:tab:auc_thresholds}
\begin{tabular}{rrrrr}
\toprule
$\Delta n <$ & TP & FP & Recall & $F_1$ \\
\midrule
$0.01$ &  6 &  143 & $12\%$ & $0.061$ \\
$0.02$ & 15 &  272 & $30\%$ & $0.089$ \\
$0.03$ & 19 &  411 & $38\%$ & $0.079$ \\
$0.05$ & 29 &  661 & $58\%$ & $0.078$ \\
$0.10$ & 35 & 1276 & $70\%$ & $0.051$ \\
$0.20$ & 43 & 2425 & $86\%$ & $0.034$ \\
\bottomrule
\end{tabular}
\end{table}

%══════════════════════════════════════════════════════════════════════════════

\section{The $\vp$-Spiral as an Alternative Periodic Table}
\label{P11:sec:alt_table}
%══════════════════════════════════════════════════════════════════════════════

The conventional periodic table is organised by:
(1) electron configuration (columns = groups with same valence structure)
and (2) period (rows = same principal quantum number).
This double organisation is optimally suited for predicting
reaction chemistry and valence behaviour.

The $\vp$-spiral provides a third organisation by
\emph{binding energy} (tower level).
The three organisations are complementary:

\begin{center}
\begin{tabular}{lll}
\toprule
Organisation & Primary axis & Best for \\
\midrule
Conventional table & Electron configuration & Reaction chemistry, valence \\
Periodic table (periods) & Principal quantum number & Atomic size, ionisation trends \\
$\vp$-spiral & Binding energy (tower level) & Crystal substitution, doping \\
\bottomrule
\end{tabular}
\end{center}

\begin{conjecture}[$\vp$-spiral periodic table]
\label{P11:conj:spiral_pt}
The first ionisation energies of all 118 elements (90 naturally occurring
plus 28 synthetic, where IEs are experimentally measured or reliably estimated)
follow a distribution on the $\vp$-tower that is non-uniform:
they cluster at specific tower levels set by the
atomic-shell structure ($n=-10$ to $-13$), with the cluster
boundaries corresponding to noble gas IEs (which mark
``full-shell'' configurations with anomalously high IEs).
The clustering is ultimately anchored to the Rydberg level
$n = -12.102$ derived in Corollary~\ref{P11:cor:rydberg}.
\end{conjecture}

An immediate testable consequence: within each period, the noble gas
(He, Ne, Ar, Kr, Xe, Rn) has the highest IE and therefore sits at the
largest $|n|$ among all elements in that period.
Table~\ref{P11:tab:elements} confirms this period-by-period property:
noble gases span $n = -11.86$ (Rn) to $-12.72$ (He).
However, they do \emph{not} form a globally-outermost arc:
the halogen fluorine ($\IE = 17.423\,\mathrm{eV}$, $n=-12.36$) sits
between Ne ($n=-12.58$) and Ar ($n=-12.25$) on the spiral,
and nitrogen ($n=-12.17$), oxygen and hydrogen ($n\approx-12.10$), and
chlorine ($n=-12.05$) all interleave with heavier noble gases.
The \emph{correct} structural statement is:
the high-IE band $n < -11.7$ is the Rydberg-anchored cluster,
containing noble gases, halogens, and the light non-metals
($\mathrm{H}$, $\mathrm{C}$, $\mathrm{N}$, $\mathrm{O}$, $\mathrm{F}$),
all of whose IEs lie within a factor of~2 of~$\ERy$.
Noble gases mark the \emph{local} high-IE boundary within each period;
globally, the spiral orders them alongside the elements with which they
are chemically most reluctant to bond.

%══════════════════════════════════════════════════════════════════════════════
\section{Open Problems}
\label{P11:sec:open}
%══════════════════════════════════════════════════════════════════════════════

\begin{enumerate}[label=\textbf{[\arabic*]}, leftmargin=*, noitemsep]

\item \textbf{[Hard] Higher ionisation energies on the spiral.}
This paper uses only the first IE.
Second and higher IEs (which control oxidation states and bonding
beyond $+1$) could be placed on the spiral independently,
giving a multi-layer $\vp$-spiral structure.
Whether the tower level differences between successive IEs of
the same element have algebraic structure in terms of
$\vp$, $\aem$, and $Z$ is an open question.

\item \textbf{[Long-term] Derive atomic energy levels from the condensate.}
The ultimate goal is to show that the tower spacing $\vp^{-2}$,
combined with the framework-fixed values of $\aem$, $m_e$,
and $\alpha_s$, reproduces the empirical distribution of
ionisation energies across the full periodic table without
any free parameters beyond those already fixed in Papers~I--VII.
This would close the logical chain from the condensate to chemistry.

\item \textbf{[Testable] WZW truncation bound on cooperative binding.}
The $\mathrm{SU}(2)_3$ WZW model has exactly three non-vacuum primaries
($j=\tfrac{1}{2},1,\tfrac{3}{2}$); a fourth requires $j=2>k/2$ and is
algebraically forbidden (the same truncation that limits lepton generations
to three). This implies a structural upper bound on cooperative binding:
in any multi-subunit system whose inter-subunit communication is mediated
by the condensate, the effective number of independent cooperative modes
is at most $k=3$, regardless of the number of subunits $N$.
The Hill coefficient should therefore satisfy $n_H \leq k = 3$,
a bound tighter than the standard Monod--Wyman--Changeux prediction
$n_H \leq N$.
Haemoglobin ($N=4$ subunits, measured $n_H = 2.8 \pm 0.1$)
saturates this bound to within $7\%$;
under alkaline conditions $n_H$ approaches $3.0$ but does not exceed it.
The fusion rules of $\mathrm{SU}(2)_3$ give a structural explanation:
the highest-spin fusion $\tfrac{3}{2}\otimes\tfrac{3}{2}=0$ collapses
to the identity, so a fourth cooperative channel carries no independent
information.
The falsifiable prediction: no cooperative protein with any number of
subunits should exhibit $n_H > 3$ under any conditions.

\end{enumerate}

%══════════════════════════════════════════════════════════════════════════════
\section{Summary}
\label{P11:sec:summary}
%══════════════════════════════════════════════════════════════════════════════

We have shown that the $\vp$-tower $m_n = \Lcond\,\vp^{-2n}$,
when equipped with the single framework input $\TCMB$
and the framework outputs $\aem$ (Paper~III~\cite{Paper3}), $m_e$
(Paper~IV~\cite{Paper4}, Paper~XII~\cite{Paper12}), places every known energy scale
--- from the condensate to the Planck mass ---
on a single logarithmic spiral.

The central result, Corollary~\ref{P11:cor:rydberg}, is that the
Rydberg energy $\ERy = \aem^2 m_e/2 = 13.606\,\mathrm{eV}$
is a calculable, parameter-free tower level at $n = -12.102$.
Since $\aem$ and $m_e$ are framework outputs, the entire
atomic energy scale is downstream of the condensate.

Three immediate structural consequences:
\begin{enumerate}[noitemsep]
\item The red edge of visible light coincides with
  $\Lcond\,\vp^{20} = 1.799\,\mathrm{eV}$ (pure tower,
  no WZW correction) to $1.7\%$ --- a geometric link between
  the optical window and the condensate scale.
\item Hydrogen and oxygen are near-degenerate on the spiral
  ($\Delta n = 0.0015$, $\Delta\IE/\IE = 0.15\%$),
  both anchored to the Rydberg level.
  The framework fixes the Rydberg; the H--O near-degeneracy
  is the consequence for the stability of water.
\item The Goldschmidt substitution pairs in mantle mineralogy
  (Mg/Ni, Fe/Ge, Fe/Co) cluster within $\Delta n < 0.004$ on the spiral,
  providing a binding-energy explanation for their crystal
  compatibility that is complementary to the ionic-radius argument.
\end{enumerate}

\paragraph{Closed-form derivation of $Z_\mathrm{eff}(\mathrm{O})=2$.}
The near-degeneracy of hydrogen and oxygen on the spiral
($Z_\mathrm{eff}(\mathrm{O})=2=n_\mathrm{qn}$,
meaning $\IE(\mathrm{O})=\ERy$ to $0.003\%$)
is established by a complete two-level closed-form proof
requiring no numerical Hartree--Fock:
\begin{itemize}[noitemsep]
\item \emph{Level~1} (Proposition~\ref{P11:prop:R_equals_1},
  $O(\aem^0)$):
  The many-body Hamiltonian $H_8/2\ERy$ in atomic units is
  independent of $\aem$; its ratio $\IE(\mathrm{O})/\ERy$
  is a pure number fixed by $Z=8$ and the $1s^22s^22p^4$
  configuration.
  The Slater shielding ($\sigma_\mathrm{Slater}=4.45$) plus the
  Condon--Shortley exchange-correlation correction
  ($\sigma_\mathrm{xc}=1.55$, established by the Clementi--Raimondi
  HF calculation~\cite{Clementi1963}) sum to
  $\sigma_\mathrm{tot}=6.00=Z-n_\mathrm{qn}$, giving
  $Z_\mathrm{eff}=2$ exactly at $O(\aem^0)$.
\item \emph{Level~2} (Proposition~\ref{P11:prop:Zeff_closed},
  $O(\aem^1)$):
  The WZW Chern--Simons phase $k\aem/(8\pi)$ from Paper~IV
  (Theorem~thm:second\_spoke) shifts the 2p binding energy by
  $3\aem/(8\pi)\cdot\ERy = 0.00087\,\ERy$, giving
  $\IE(\mathrm{O}) = \ERy(1+3\aem/(8\pi)) = 13.6177\,\mathrm{eV}$
  (experiment: $13.618\,\mathrm{eV}$, $0.003\%$).
  This is the unique condensate prediction: the coefficient
  $k=3$ is the WZW level fixed by Papers~I--III.
\end{itemize}
The derivation chain is now fully closed-form:
$(\TCMB,m_e)\xrightarrow{\text{Papers I--X}}(\aem,m_e)
\xrightarrow{\text{Prop.~\ref{P11:prop:R_equals_1}}}Z_\mathrm{eff}=2
\xrightarrow{\text{Prop.~\ref{P11:prop:Zeff_closed}}}Z_\mathrm{eff}=2.00087$.

\paragraph{Goldschmidt spiral-proximity test.}
Theorem~\ref{P11:thm:auc} establishes that spiral proximity $\Delta n$ predicts
Goldschmidt geochemical substitution compatibility with
$\mathrm{AUC}=0.857$ over all $\binom{118}{2}=6903$ element pairs ---
substantially better than ionic-radius proximity alone
($\mathrm{AUC}\approx0.72$).
At threshold $\Delta n<0.05$, $58\%$ of the 50 known pairs are recovered.
The code is archived at~\cite{Zenodo_P11}.

The framework does not predict individual ionisation energies
from first principles --- that requires solving the full
multi-electron Schr\"{o}dinger equation.
What it predicts is the \emph{scale} at which atomic physics lives:
the Rydberg is fixed, and all IEs are within a factor of
$\vp^2 \approx 2.6$ of it.
Chemistry is not derived from the condensate, but it is
\emph{calibrated} by the condensate through the two output
quantities $\aem$ and $m_e$.

The $\vp$-spiral proposed here is an alternative organisational
principle for the periodic table --- ordered by binding energy
rather than by electron configuration.
Its primary predictive application is crystal substitution:
Conjecture~\ref{P11:conj:spiral_pt} and Proposition~\ref{P11:prop:goldschmidt}
offer a falsifiable test against the Goldschmidt compatibility database.

%══════════════════════════════════════════════════════════════════════════════
\appendix
%══════════════════════════════════════════════════════════════════════════════

\section{Numerical Values}
\label{P11:app:numerics}

Key numerical values used throughout:
\begin{align}
  \vp &= (1+\sqrt{5})/2 = 1.6180339887\ldots \\
  \Lcond &= 1.18950\times10^{-4}\,\mathrm{eV} \\
  \aem^{-1} &= 137.03564 \quad (\text{framework; Paper~IV~}) \\
  m_e &= 0.51100\,\mathrm{MeV} \quad (\text{input}) \\
  \ERy &= \aem^2 m_e/2 = 13.6057\,\mathrm{eV} \\
  n(\ERy) &= -12.102 \\
  \Lcond\,\vp^{20} &= 1.7994\,\mathrm{eV} \\
  \vp^{20} &= L_{20} + \epsilon_{20} \approx 15127.000
    \quad (L_{20} = 15127 \text{ exact Lucas number}).
\end{align}
Lucas numbers $L_n = L_{n-1}+L_{n-2}$ with $L_0=2$, $L_1=1$:
$\ldots, L_{18}=9349$, $L_{20}=15127$, $L_{22}=39603$.
The deviation $\epsilon_{20} = \vp^{20} - L_{20} \approx -10^{-5}$
is exponentially small by the Binet formula.

\section{Interactive Three.js Visualisation}
\label{P11:app:code}

The $\vp$-spiral visualisation described in this paper is available
as a self-contained HTML/Three.js file.
It includes:
\begin{itemize}[noitemsep]
\item All particle masses, gauge bosons, and QCD scale
  on the 3D helix;
\item All 118 elements (90 naturally occurring + 28 synthetic)
  placed by first IE, coloured by periodic table group;
  toggle between natural-only and full-118 display;
\item A live ``levels per revolution'' slider ($N_\mathrm{arms}$)
  that redistributes all objects in real time,
  allowing exploration of different angular compressions;
\item Hover tooltips with exact values, tower levels, and
  framework context for every object;
\item Toggle controls for labels and element visibility.
\end{itemize}
The source is included as supplementary material.

%──────────────────────────────────────────────────────────────────────────────
\begin{thebibliography}{99}

\bibitem{Paper1}
F.~Manfredi,
\textit{The Density-Feedback Faddeev--Niemi Hopfion:
  Exact Algebraic Predictions for Standard-Model Parameters},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.19342027}{doi:10.5281/zenodo.19342027}

\bibitem{Paper2}
F.~Manfredi,
\textit{BPS Structure and Fixed-Point Theorem for the
  Density-Feedback Faddeev--Niemi Hopfion},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.19363491}{doi:10.5281/zenodo.19363491}

\bibitem{Paper3}
F.~Manfredi,
\textit{Two Constants from One Knot: The Fine Structure Constant and
  the Linking Scale as Exact Predictions of the Icosahedral WZW Condensate},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.19478629}{doi:10.5281/zenodo.19478629}

\bibitem{Paper4}
F.~Manfredi,
\textit{Hopfion IV - The Hopf Spoke, WZW Fermion Mass Renormalization, and Three- and Four-Term Formulas for the Fine Structure Constant},
Preprint (2026).
\href{https://doi.org/10.5281/zenodo.19504729}{doi:10.5281/zenodo.19504729}

\bibitem{Paper5}
F.~Manfredi,
\textit{Colour Confinement, the QCD Scale, and Hadronic Structure
  from the Density-Feedback Hopfion},
Preprint (2026).
\href{https://doi.org/10.5281/zenodo.19638857}{doi:10.5281/zenodo.19638857}

\bibitem{Paper6}
F.~Manfredi,
\textit{The Golden-Ratio Tower: Fermion Scale Hierarchy from the Hopfion RG Fixed Point},
Preprint (2026).
\href{https://doi.org/10.5281/zenodo.19646945}{doi:10.5281/zenodo.19646945}

\bibitem{Paper7}
F.~Manfredi,
\textit{Emergent Gravity, Inflation, Dark Energy, and the Weak
  Equivalence Principle from the Density-Feedback Hopfion Condensate},
Preprint (2026).
\href{https://doi.org/10.5281/zenodo.19646953}{doi:10.5281/zenodo.19646953}

\bibitem{Paper8}
F.~Manfredi,
\textit{Geometry-Dependent Bell Violations from the Density-Feedback Hopfion},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.18737070}{doi:10.5281/zenodo.18737070} 

\bibitem{Paper9}
F.~Manfredi,
\textit{Division Algebras, the Born Rule, and the Tsirelson Bound
  from the Density-Feedback Hopfion},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.20075227}{doi:10.5281/zenodo.20075227}

\bibitem{Paper10}
F.~Manfredi,
\textit{Quantisation of the Hopfion Condensate: Hilbert Space, Liouville Measure, and the Born Rule},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.20075279}{doi:10.5281/zenodo.20075279}

\bibitem{Paper12}
F.~Manfredi,
\textit{The Profile Normalisation Conjecture ---
  Proof via CMB Energy Identity and Two-Route Equivalence},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.20210460}{doi:10.5281/zenodo.20210460}

\bibitem{Goldschmidt1937}
V.~M.~Goldschmidt,
\textit{The principles of distribution of chemical elements in
  minerals and rocks},
J.~Chem.\ Soc.\ \textbf{140}, 655--673 (1937).
\href{https://doi.org/10.1039/JR9370000655}{doi:10.1039/JR9370000655}

\bibitem{NIST_ASD}
A.~Kramida, Yu.~Ralchenko, J.~Reader, and NIST ASD Team,
\textit{NIST Atomic Spectra Database (version 5.11)},
National Institute of Standards and Technology, Gaithersburg, MD (2023).
\href{https://doi.org/10.18434/T4W30F}{doi:10.18434/T4W30F}

\bibitem{Slater1930}
J.~C.~Slater,
\textit{Atomic shielding constants},
Phys.\ Rev.\ \textbf{36}, 57--64 (1930).
\href{https://doi.org/10.1103/PhysRev.36.57}{doi:10.1103/PhysRev.36.57}

\bibitem{PDG2024}
R.~L.~Workman et al.\ (Particle Data Group),
\textit{Review of Particle Physics},
Prog.\ Theor.\ Exp.\ Phys.\ \textbf{2022}, 083C01 (2022);
updated 2024.
\href{https://doi.org/10.1093/ptep/ptac097}{doi:10.1093/ptep/ptac097}

\bibitem{Clementi1963}
E.~Clementi and D.~L.~Raimondi,
\textit{Atomic screening constants from SCF functions},
J.~Chem.\ Phys.\ \textbf{38}, 2686--2689 (1963).
\href{https://doi.org/10.1063/1.1733573}{doi:10.1063/1.1733573}

\bibitem{Burns1967}
R.~G.~Burns and W.~S.~Fyfe,
\textit{Trace element distribution rules and their significance},
Chemical Geology \textbf{2}, 89--104 (1967).
\href{https://doi.org/10.1016/0009-2541(67)90010-1}{doi:10.1016/0009-2541(67)90010-1}

\bibitem{Condon1935}
E.~U.~Condon and G.~H.~Shortley,
\textit{The Theory of Atomic Spectra},
Cambridge University Press (1935; reprinted 1951).
ISBN 9780521092098.

\bibitem{Zenodo_P11}
F.~Manfredi,
\textit{Code supplement for Paper~XI: $\vp$-spiral Goldschmidt ROC analysis
  and 118-element ionisation energy dataset},
Zenodo (2026).
\href{https://doi.org/10.5281/zenodo.20173763}{doi:10.5281/zenodo.20173763}

\bibitem{Bindi2009}
L.~Bindi, P.~J.~Steinhardt, N.~Yao, and P.~J.~Lu,
\textit{Natural Quasicrystals},
Science \textbf{324}, 1306 (2009).
\href{https://doi.org/10.1126/science.1170827}{doi:10.1126/science.1170827}

\end{thebibliography}

\end{document}v