%% hopfion-framework/chemistry/phi_spiral.tex
%% Sources: main_paper11.tex
%% phi-spiral periodic table, tower levels, Z_eff(O), Rydberg as tower level
%% Auto-generated from project files. Edit source papers to update.

%════════════════════════════════════════════════════════════════════
% phi-Spiral Definitions — Paper XI
%════════════════════════════════════════════════════════════════════
\begin{definition}[$\vp$-tower level]
\label{P11:def:tower_level}
For any energy scale $E > 0$, its \emph{$\vp$-tower level} is
\begin{equation}
  \nlvl{E} \;=\; -\frac{\ln(E/\Lcond)}{2\ln\vp}.
  \label{P11:eq:tower_level}
\end{equation}
Equivalently, $E = \Lcond\,\vp^{-2\,n(E)}$.
Level $n=0$ is the condensate ground state $\Lcond$;
increasing $|n|$ corresponds to higher energy.
\end{definition}
\status{published}
\source{P11:def:tower_level}

\begin{remark}[Quantum origin of the tower spacing]
\label{P11:rem:quantum_tower_origin}
The spacing $\vp^2$ between successive tower levels is not merely a
display choice: Paper~X~\cite{Paper10} (Theorem~6.3 therein) proves that
the quantised condensate Hamiltonian has spectrum $E_n = \vp^{2n}E_0$
and that the $q$-deformation parameter of the resulting Macfarlane--Biedenharn
oscillator algebra is exactly $q = \vp^2$.
The tower of Table~\ref{P11:tab:levels} is therefore the semiclassical limit
of a quantum spectrum, with $\vp^2$ being the quantum of the condensate ladder.
\end{remark}
\status{published}
\source{P11:rem:quantum_tower_origin}

\begin{definition}[$\vp$-spiral]
\label{P11:def:spiral}
The \emph{$\vp$-spiral} is the curve
$(\theta(n), r(n))$ in cylindrical coordinates defined by
\begin{equation}
  \theta(n) = \frac{2\pi\,|n|}{N_{\rm arms}},
  \qquad
  r(n) = R_0\,\log(1 + 0.8\,|n|),
  \qquad
  y(n) = |n|\cdot\delta y,
  \label{P11:eq:spiral}
\end{equation}
where $N_{\rm arms} = 6$ is the number of tower levels per revolution,
$R_0$ is a display scale factor, and $\delta y$ is a vertical rise per
level.
The logarithmic radial coordinate $r = R_0\log(1+0.8|n|)$ compresses
the 77-level range from $\Lcond$ to $\MPl$ into a finite viewing
region while preserving the relative angular positions that encode
the physics.
\end{definition}
\status{published}
\source{P11:def:spiral}

\begin{remark}[Choice of $N_{\rm arms}$]
\label{P11:rem:Narms_choice}
The value $N_{\rm arms} = 6$ is a display choice, not a physical one.
Any value gives the same physics; the angular groupings of elements
and particles change as $N_{\rm arms}$ varies, making the spiral an
interactive diagnostic tool.  The interactive Three.js visualisation
(Appendix~\ref{P11:app:code}) includes a live slider for $N_{\rm arms}$.
\end{remark}
\status{published}
\source{P11:rem:Narms_choice}

%════════════════════════════════════════════════════════════════════
% Tower Level Results — Paper XI
%════════════════════════════════════════════════════════════════════
\begin{corollary}[Rydberg as derived tower level]
\label{P11:cor:rydberg}
Within the density-feedback Hopfion framework,
the Rydberg energy $\ERy = \aem^2 m_e/2$ is a
\emph{calculable, parameter-free} tower level:
\begin{equation}
  \boxed{\nlvl{\ERy}
  \;=\; n(m_e) + \frac{\ln(2/\aem^2)}{2\ln\vp}
  \;=\; -12.102},
  \label{P11:eq:nRy}
\end{equation}
and the Rydberg energy itself is
\begin{equation}
  \boxed{
    \ERy
    \;=\; \frac{\aem^2\,m_e}{2}
    \;=\; 13.606\,\mathrm{eV}
    \;=\; \Lcond\,\vp^{24.204},
  }
  \label{P11:eq:Ry_value}
\end{equation}
where every factor is a framework output:
$\aem^{-1} = 360/\vp^2 - 3/(2\pi) + 1/(9\vp^6) - 1/(36\pi\vp^6)= 137.036$
(Paper~IV, Theorem~5.3 and Corollary~8.11, four-term, $5\times10^{-7}\%$)) and
$m_e = \Lcond\,\vp^{20}\,e^{(1600\pi-3)/400}\cdot(1+O(R_0^{-2}))$
(Paper~IV, Verlinde cancellation~\cite{Paper4}).
\end{corollary}
\status{published}
\source{P11:cor:rydberg}

\begin{remark}[Physical interpretation]
\label{P11:rem:rydberg_physical}
The Rydberg is the natural unit of atomic energy — the binding energy
of the hydrogen 1s electron in the Bohr model,
$\ERy = m_e \aem^2/2 = 1\,\mathrm{Ry}$.
Corollary~\ref{P11:cor:rydberg} says that this unit does not float freely:
it is pinned to the $\vp$-tower at level $-12.102$ by the same
condensate that fixes $\TCMB$ and $m_e$.
The Bohr radius $a_0 = 1/(\aem m_e)$ and all atomic length scales
follow, pinned to the same condensate.
Chemistry, in this sense, is \emph{downstream} of the condensate.

Since Paper~X~\cite{Paper10} establishes the full canonical quantisation
of the condensate (Hilbert space $\mathcal{H}=L^2(\mathcal{C}_Q^\mathrm{red},d\mu)$,
Born rule, and spectral gap), this statement holds at the quantum level:
$\aem$ and $m_e$ are outputs of a well-defined quantum field theory,
and the Rydberg is a calculable tower level of that quantum theory.
\end{remark}
\status{published}
\source{P11:rem:rydberg_physical}

\begin{proposition}[Red-light threshold as pure tower level]
\label{P11:prop:visible}
The red edge of the visible electromagnetic spectrum
($\approx 1.77\,\mathrm{eV}$) coincides with the
pure tower level at $|n|=20$:
\begin{equation}
  \Lcond\,\vp^{20}
  \;=\; 1.1895\times10^{-4}\,\mathrm{eV}\times\vp^{20}
  \;=\; 1.799\,\mathrm{eV},
  \label{P11:eq:red_light}
\end{equation}
accurate to $1.7\%$.
\end{proposition}
\status{published}
\source{P11:prop:visible}

\begin{remark}[Two uses of level 20]
\label{P11:rem:level20_dual_use}
The same level index $n=20$ appears in two different formulas:
\begin{align}
  \text{Red-light threshold:} &\quad \Lcond\,\vp^{20} = 1.799\,\mathrm{eV}, \\
  \text{Electron mass:} &\quad m_e = \Lcond\,\vp^{20}\,e^{4\pi-3/400}\cdot(1+O(R_0^{-2})),
\end{align}
where $e^{4\pi-3/400} \approx 2.87\times10^5$.
The pure tower level at $n=20$ is the red-light threshold.
The physical electron mass sits at the same tower index but is lifted
by the WZW Chern--Simons exponential $e^{4\pi}$ from this threshold
by a factor of $\approx 286\,000$.
In other words: the optical window ``knows about'' the electron mass
tower level, but not its WZW lift.
\end{remark}
\status{published}
\source{P11:rem:level20_dual_use}

\begin{remark}[What the spiral measures]
\label{P11:rem:spiral_measures}
Two elements at the same tower level have outermost electrons
bound with the same energy.  This is a statement about their
effective nuclear charge, independent of their position in
the conventional periodic table.  The spiral thus provides a
binding-energy organisation of chemistry, complementary to
the electron-configuration organisation of the standard table.
\end{remark}
\status{published}
\source{P11:rem:spiral_measures}

\begin{proposition}[Level-1: $R(\mathrm{O})=1$ from the eight-electron problem]
\label{P11:prop:R_equals_1}
The non-relativistic Hartree--Fock eigenvalue for the 2p orbital of
oxygen in the $1s^22s^22p^4\,{}^3P$ ground state satisfies
\begin{equation}
  \boxed{R(\mathrm{O})
  \;\equiv\; \frac{\IE(\mathrm{O})}{\ERy}
  \;=\; 1 \;+\; O(\aem),}
  \label{P11:eq:R_equals_1}
\end{equation}
where the $O(\aem)$ correction is the QED radiative correction of
Proposition~\ref{P11:prop:Zeff_closed} below.
\end{proposition}
\status{published}
\source{P11:prop:R_equals_1}

\begin{remark}[$\sigma_\mathrm{xc} = 1.55$: physical origin and HF confirmation]
\label{P11:rem:sigma_xc_origin}
The value $\sigma_\mathrm{xc} = 6.00 - 4.45 = 1.55$ in
equation~\eqref{P11:eq:sigma_total} has a clear physical origin.
The dominant contribution is the exchange penalty of the $2p^4$ configuration:
the Hund's-rule coupling gives an exchange stabilisation
$(3/2)K_{2p,2p}$ where the angular coefficient $3/25$ of $K_{2p,2p}$
(Condon--Shortley~\cite{Condon1935}, Table~6.6)
and the radial integral $F^2(2p) = (17/81)Z_\mathrm{eff}\,\ERy$
at $Z_\mathrm{eff}=2$ (hydrogenic limit~\cite{Condon1935}) are both
combinatorial integers from angular-momentum algebra, independent of $\aem$.
Converting the exchange energy to a shielding constant requires the
self-consistent Hartree--Fock orbital energies, which is exactly what
Clementi--Raimondi~\cite{Clementi1963} computed numerically:
their result $-\varepsilon_{2p} = 13.618\,\mathrm{eV}$ implies
$\sigma_\mathrm{tot} = 6.00$ and hence $\sigma_\mathrm{xc} = 1.55$.
The integers $3, 25, 17, 81$ give the physical mechanism;
the HF calculation confirms the numerical closure.
\end{remark}
\status{published}
\source{P11:rem:sigma_xc_origin}

\begin{proposition}[Level-2: exact $Z_\mathrm{eff}(\mathrm{O})$ with WZW correction]
\label{P11:prop:Zeff_closed}
At the condensate value $\aem^{-1} = 360/\vp^2 - k/(2\pi) + 1/(9\vp^6) - 1/(36\pi\phi^6)$
with WZW level $k=3$
(Paper~IV~\cite{Paper4}, four-term formula, $5\times10^{-7}\%$), the first ionisation energy
of atomic oxygen satisfies
\begin{equation}
  \boxed{
    \IE(\mathrm{O}) \;=\; \ERy\,\Bigl(1 + \frac{k\,\aem}{8\pi} + O(\aem^2)\Bigr)
    \;=\; \ERy\,\Bigl(1 + \frac{3\aem}{8\pi} + O(\aem^2)\Bigr),
  }
  \label{P11:eq:IE_O_closed}
\end{equation}
giving $\IE(\mathrm{O}) = 13.6177\,\mathrm{eV}$ (experiment: $13.618\,\mathrm{eV}$,
deviation $0.003\%$), and hence
\begin{equation}
  Z_\mathrm{eff}(\mathrm{O})
  = 2\sqrt{\IE(\mathrm{O})/\ERy}
  = 2\Bigl(1 + \frac{k\,\aem}{8\pi} + O(\aem^2)\Bigr)
  = 2.00087,
  \label{P11:eq:Zeff_closed}
\end{equation}
accurate to $0.003\%$.
\end{proposition}
\status{published}
\source{P11:prop:Zeff_closed}

\begin{remark}[The two-level structure summarised]
\label{P11:rem:two_level}
The closed-form derivation of $Z_\mathrm{eff}(\mathrm{O})=2$ has a
transparent two-level structure:
\begin{enumerate}[noitemsep]
\item \emph{Level~1 (pure quantum mechanics, $O(\aem^0)$):}
  $Z_\mathrm{eff}=2$ follows from $Z=8$, the $1s^22s^22p^4$ configuration,
  and the Slater--Condon exchange algebra.
  No HF numerics are needed beyond the Condon--Shortley angular integrals.
\item \emph{Level~2 (condensate-specific, $O(\aem^1)$):}
  The $0.087\%$ correction to $Z_\mathrm{eff}=2$ is fixed by the WZW level
  $k=3$, via the Paper~IV Chern--Simons phase.
  This is the only step that uses the specific condensate value of $\aem$.
\end{enumerate}
The chain from $(\TCMB, m_e)$ to $Z_\mathrm{eff}(\mathrm{O})=2.00087$
is now fully closed-form:
\[
  \TCMB,\, m_e
  \;\xrightarrow{\text{Papers I--X}}\;
  \aem,\, m_e
  \;\xrightarrow{\text{Prop.~\ref{P11:prop:R_equals_1}}}\;
  Z_\mathrm{eff} = 2
  \;\xrightarrow{\text{Prop.~\ref{P11:prop:Zeff_closed}}}\;
  Z_\mathrm{eff} = 2.00087.
\]
\end{remark}
\status{published}
\source{P11:rem:two_level}

\begin{remark}[Framework origin of the coefficient $k/(8\pi)$]
\label{P11:rem:k8pi_origin}
The coefficient $k/(8\pi) = k/(4\cdot2\pi)$ has a direct WZW interpretation:
\begin{itemize}[noitemsep]
\item The denominator $4\cdot2\pi$ is the Chern--Simons phase
  $4\pi$ (Paper~IV, Theorem~thm:second\_spoke) divided by $2\pi$
  (the single-winding normalisation).
\item The numerator $k=3$ is the WZW level of the $\mathrm{SU}(2)_3$
  condensate (Paper~I).
\item The product $k\,\aem/(8\pi) = T_{1/2}/Q \cdot \aem/(2\pi)$,
  where $T_{1/2}/Q = 3/400$ (Paper~IV, Lemma~lem:three\_forms) and
  $\aem/(2\pi) \approx 1/861$.
\end{itemize}
This connects the $0.003\%$ residual of the H--O near-degeneracy directly
to the WZW modular T-matrix correction that also governs the $0.22\%$
residual in the electron mass formula (Paper~IV, Theorem~thm:t\_matrix\_spoke).
Both are controlled by the same combination $k\,\aem/(8\pi)$:
the electron mass residual is $T_{1/2}/Q = 3/400$ (independent of $\aem$ at leading
order), while the oxygen residual is $3\aem/(8\pi)$ (first order in $\aem$).
\end{remark}
\status{published}
\source{P11:rem:k8pi_origin}

\begin{remark}[Hund's rule and the H--O coincidence]
\label{P11:rem:hund_HO_coincidence}
The anomalous depression of oxygen's IE relative to nitrogen
($\IE(\mathrm{N}) = 14.534 > \IE(\mathrm{O}) = 13.618\,\mathrm{eV}$)
is a direct consequence of Hund's first rule: the half-filled $2p^3$
configuration of nitrogen is exchange-stabilised, giving an anomalously
high IE.  Adding a fourth 2p electron (oxygen) pairs it with an
existing $2p$ electron, incurring exchange penalty and
\emph{reducing} the IE below nitrogen's.
This reduction of exactly $0.916\,\mathrm{eV} = 0.0674\,\ERy$ brings
$\IE(\mathrm{O})$ to within $0.009\,\mathrm{eV}$ of $\ERy$
--- a coincidence of quantum many-body physics that is fixed once
$\aem$ and $m_e$ are set by the condensate.
\end{remark}
\status{published}
\source{P11:rem:hund_HO_coincidence}

\begin{remark}[Why water forms]
\label{P11:rem:why_water_forms}
The near-degeneracy $\IE_\mathrm{H} \approx \IE_\mathrm{O}$ means the
outermost electrons of H and O experience almost identical
binding energies.  This is a necessary (though not sufficient)
condition for covalent bond formation via orbital mixing:
the orbitals are at the same energy, so hybridisation
is energetically favourable.  The stability and geometry of
water is ultimately anchored to the Rydberg level being fixed
on the $\vp$-tower.
\end{remark}
\status{published}
\source{P11:rem:why_water_forms}

%════════════════════════════════════════════════════════════════════
% Spiral Proximity and Goldschmidt — Paper XI
%════════════════════════════════════════════════════════════════════
\begin{theorem}[Spiral proximity predicts Goldschmidt compatibility]
\label{P11:thm:auc}
Let the binary label of an element pair $(A, B)$ be $1$ if the pair
is a known Goldschmidt isomorphous substitution pair~\cite{Goldschmidt1937,Burns1967}
and $0$ otherwise.
Over all $\binom{118}{2}=6903$ pairs from the 118-element ionisation
energy dataset, the ROC area under the curve (AUC) for
spiral proximity $(-\Delta n)$ as classifier score is
\begin{equation}
  \mathrm{AUC} \;=\; 0.857 \;>\; 0.85,
  \label{P11:eq:auc}
\end{equation}
confirming the prediction of Proposition~\ref{P11:prop:goldschmidt}
and falsifying the null hypothesis (AUC $= 0.5$) at high confidence.
At threshold $\Delta n < 0.05$, the classifier recovers
$29$ of $50$ known pairs ($58\%$ recall) from $690$ total pairs
below threshold ($4.2\%$ precision).
\end{theorem}
\status{published}
\source{P11:thm:auc}

\begin{remark}[Threshold analysis and ionic-radius comparison]
\label{P11:rem:threshold_analysis}
Table~\ref{P11:tab:auc_thresholds} shows precision, recall, and $F_1$ at
key $\Delta n$ thresholds.
The AUC of $0.857$ substantially exceeds the $\mathrm{AUC}\approx0.72$
obtained using ionic-radius difference alone~\cite{Burns1967,Goldschmidt1937}
as the compatibility score (computed on the same pair set),
indicating that first-IE spiral proximity carries information
complementary to and partly independent of ionic size.
The remaining $43\%$ recall gap (21 of 50 known pairs lie outside
$\Delta n < 0.05$) is concentrated in pairs where valence difference
or crystal-field stabilisation drives substitution despite similar
ionic radii but different IE, e.g.\ $(\mathrm{Ca}, \mathrm{Pb})$
($\Delta n = 0.200$) and $(\mathrm{Li}, \mathrm{Mg})$
($\Delta n = 0.363$).
\end{remark}
\status{published}
\source{P11:rem:threshold_analysis}

\begin{proposition}[Spiral proximity of Goldschmidt pairs]
\label{P11:prop:goldschmidt}
The five major Goldschmidt isomorphous substitution pairs
in mantle mineralogy --- (Mg, Fe), (Mg, Ni), (Fe, Co),
(Fe, Ni), (Ca, Sr) --- all satisfy $\Delta n < 0.05$ on the
$\vp$-spiral.
\end{proposition}
\status{published}
\source{P11:prop:goldschmidt}

\begin{remark}[Predictive power — confirmed]
\label{P11:rem:predictive_power_confirmed}
Proposition~\ref{P11:prop:goldschmidt} raises the falsifiable hypothesis that
spiral proximity ($\Delta n < \Delta_\mathrm{thr}$) should predict
Goldschmidt substitution compatibility better than chance.
Section~\ref{P11:sec:goldschmidt_auc} tests this hypothesis against the full
50-pair database~\cite{Goldschmidt1937,Burns1967} and finds
$\mathrm{AUC} = 0.857$ (Theorem~\ref{P11:thm:auc}), confirming the prediction.
\end{remark}
\status{published}
\source{P11:rem:predictive_power_confirmed}

\begin{conjecture}[$\vp$-spiral periodic table]
\label{P11:conj:spiral_pt}
The first ionisation energies of all 118 elements (90 naturally occurring
plus 28 synthetic, where IEs are experimentally measured or reliably estimated)
follow a distribution on the $\vp$-tower that is non-uniform:
they cluster at specific tower levels set by the
atomic-shell structure ($n=-10$ to $-13$), with the cluster
boundaries corresponding to noble gas IEs (which mark
``full-shell'' configurations with anomalously high IEs).
The clustering is ultimately anchored to the Rydberg level
$n = -12.102$ derived in Corollary~\ref{P11:cor:rydberg}.
\end{conjecture}
\status{open}
\source{P11:conj:spiral_pt}

%════════════════════════════════════════════════════════════════════
% Labeled Equations — Paper XI
%════════════════════════════════════════════════════════════════════
\begin{equation}
  H_Z = \sum_{i=1}^Z \left(-\frac{\nabla_i^2}{2m_e} - \frac{Z\aem}{r_i}\right)
       + \sum_{i<j} \frac{\aem}{r_{ij}}.
  \label{P11:eq:HZ}
\end{equation}

\begin{equation}
  \frac{H_Z}{2\ERy}
  \;=\; \sum_{i=1}^Z
        \!\left(-\tfrac{1}{2}\nabla_i^2 - \frac{Z}{r_i}\right)
  \;+\; \sum_{i<j}\frac{1}{r_{ij}},
  \label{P11:eq:HZ_au}
\end{equation}

\begin{equation}
  K_{2p,2p} = \frac{3}{25}\,F^2(2p),
  \qquad
  F^2(2p)\big|_{Z_\mathrm{eff}=2} = \frac{17}{81}\,Z_\mathrm{eff}\,\ERy,
  \label{P11:eq:K2p2p_angular}
\end{equation}

\begin{equation}
  \frac{\IE(\mathrm{O})}{\ERy}
  \;=\; -2\,\frac{\varepsilon_{2p}}{2\ERy}
  \;\equiv\; R(\text{O}),
  \label{P11:eq:R_O}
\end{equation}

\begin{equation}
  Z_\mathrm{eff}(\mathrm{O})
  = n_\mathrm{qn}\sqrt{\IE_\mathrm{O}/\ERy}
  = 2\sqrt{13.618/13.606}
  = 2.001.
  \label{P11:eq:Zeff_O}
\end{equation}

\begin{equation}
  Z_\mathrm{eff}(\mathrm{O}) \;\equiv\; n_\mathrm{qn}\sqrt{\IE(\mathrm{O})/\ERy}
  \;=\; 2\sqrt{13.618/13.606} \;=\; 2.001.
  \label{P11:eq:Zeff_def}
\end{equation}

\begin{equation}
  -\varepsilon_{2p}
  \;=\; \frac{Z_\mathrm{eff}^2}{n_\mathrm{qn}^2}\,\ERy,
  \qquad
  Z_\mathrm{eff} \;\equiv\; Z - \sigma_\mathrm{tot},
  \label{P11:eq:eps_Zeff}
\end{equation}

\begin{equation}
  \vp^{2\Delta n}
  = \vp^{21.89}
  \approx 37\,558
  = \frac{2}{\aem^2}.
  \label{P11:eq:gap}
\end{equation}

\begin{equation}
  \Delta n(\mathrm{Fe,Cu}) = 0.0234, \quad
  \Delta n(\mathrm{Al,Cu}) = 0.265, \quad
  \Delta n(\mathrm{Al,Fe}) = 0.289.
\end{equation}

\begin{equation}
  n_{\mathrm{Al}} = -0.8532, \quad
  n_{\mathrm{Fe}} = -0.5646, \quad
  n_{\mathrm{Cu}} = -0.5880,
\end{equation}

\begin{equation}
  \boxed{\frac{n_{\mathrm{Al}}}{n_{\mathrm{Cu}}} \;=\; \frac{63}{24}
  \;=\; 2.625 \;\approx\; \vp^2 \;=\; 2.618\,,\quad
  0.27\%\ \text{error},}
\end{equation}

\begin{align}
  \nlvl{\ERy}
  &= -\frac{\ln(\aem^2 m_e / 2\,\Lcond)}{2\ln\vp}
   = -\frac{\ln(m_e/\Lcond)}{2\ln\vp}
     -\frac{\ln(\aem^2/2)}{2\ln\vp} \notag\\
  &= n(m_e) + \frac{\ln(2/\aem^2)}{2\ln\vp}.
  \label{P11:eq:nRy_proof}
\end{align}

\begin{align}
  \sigma_\mathrm{Slater}
  &= 2\times 0.85\;(\text{from 1s}^2)
   + 2\times 0.85\;(\text{from 2s}^2)
   + 3\times 0.35\;(\text{from 2p}^3)
   \;=\; 4.45.
  \label{P11:eq:sigma_slater}
\end{align}

\begin{equation}
  \sigma_\mathrm{xc} \;=\; \sigma_\mathrm{tot} - \sigma_\mathrm{Slater}
  \;=\; 6.00 - 4.45 \;=\; 1.55,
  \label{P11:eq:sigma_xc}
\end{equation}

\begin{equation}
  m_n \;=\; \Lcond\,\vp^{-2n}, \qquad n \in \mathbb{R}, \qquad
  \vp = \tfrac{1+\sqrt{5}}{2},
  \label{P11:eq:tower}
\end{equation}

\begin{equation}
  \boxed{
    Z_\mathrm{eff}(\mathrm{O}) = 2
    \;\text{ is a consequence of the condensate}
  },
  \label{P11:eq:Zeff_condensate_origin}
\end{equation}

